# CHAPTER

## Research Question 5

**What were the length distributions of the most common species (by lengths measured) discarded across time of day and fishing depths?**

### Length distributions of the discarded fish species{#id.41}

**Importing and joining data**

```{r, message = FALSE}
# Reading in length data into R
LengthImport <- read_csv("observer_lengths_mas102m.csv")

# Joining data. But only keeping the rows containing length measurements for this 
# part of the analysis. 
LengthData <- inner_join(ObserverData,
  LengthImport,
  by = c("TripID", "DragID2", "LatinNames"))
```

Of the 61 species measured **(see Chapter 3)**, measurements were done for 13 fish species in total. This was so because species measurements were only done whenever a given species presence within a given sample was 30 or more. Initially, the analysis in this chapter will zero in on the length measurements for the more common fish species measured (by count) to answer **Research Question 5** whereas ALL fish species from the data will be utilized in answering **Research Question 6**. 

**However before sub-setting the data here is a view of length measurements for ALL of the fish species measured**

```{r tab41}
# Creating species length table 
Table.4.1 <- LengthData %>% 
  group_by(LatinNames) %>% 
  dplyr::summarise(NoMeasured = n(),
    MeanLength = round(mean(Lengths)),
    MedianLength = round(median(Lengths)),
    SDLength = round(sd(Lengths)),
    MaxLength = round(max(Lengths)),
    MinLength = round(min(Lengths)),
    .groups = 'drop') %>%
  arrange(desc(NoMeasured))

# Printing table 
Table.4.1 %>% 
  kbl(caption = "All fish species length measurements with summary statistics. The species are arranged by the most measured.") %>%
  kable_classic() %>% 
  row_spec(0, bold = TRUE) %>% 
  column_spec(1, italic = T) %>%
  kable_styling(fixed_thead = T,
    bootstrap_options = "condensed")
```

All together 3,477 individual fish were measured belonging to 13 species. Of this amount *Stellifer rastrifer* (989), *Stellifer microps* (718), *Macrodon ancylodon* (480), *Nebris microps* (262), *Bagre bagre* (239) and *Cynoscion virescens* (215) were the six most common species measured (Table \@ref(tab:tab41)). These species collectively accounted for 2903 (83.5%) of the total discarded fish species measured. On the other hand, *Trichiurus lepturus* (30), *Anchoa spinifer* (30) and *Larimus breviceps* (62) were the least abundant. Fish species lengths ranged from a minimum of 2 cm (*Stellifer rastrifer* and *Stellifer microps*) to 70 cm (*Trichiurus lepturus*). The median lengths for all species except *Trichiurus lepturus* (60 cm) and *Paralonchurus elegans* (23 cm) were below 20 cm.  

### Subsetting the top 6 most common fish species measured 

After seeing the length distribution for the fish species measured (Table \@ref(tab:tab41)) we will now zoom in on the 6 most commonly measured. Before any analysis it is important to inspect the data visually. 

**Inspection of the data before analysis** 

```{r fig41, fig.asp = 0.75, fig.align = "center", fig.cap = "Scatter plot of discarded fish species lengths across bottom trawl fishing tows. A total of 48 bottom trawl fishing tows were made. No fish lengths were measured for 9 fishing trips; 12,22,24,28,30,40,43,44 & 45. " }

# Creating a vector 
length.names.top.6 <- head(Table.4.1$LatinNames, 6) 

# Filtering data
length.data.top.6 <- LengthData %>% 
  filter(LatinNames %in% length.names.top.6) 

# Plotting data
ggplot(data = length.data.top.6,
  mapping = aes(x = DragID2,
    y = Lengths, 
    color = LatinNames)) +
  geom_point(size = 1.2) +
  scale_x_continuous(breaks = seq(from = 1, to = 48)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90,
    vjust = 0.5,
    hjust= 1),
    text = element_text(size = 10),
    legend.title = element_blank(),
    legend.position = "bottom",
    legend.text = element_text(face = "italic")) +
  labs(x = "Bottom trawl fishing tows",
    y = "Lengths (cm)") +
 ## the code below are used to add the max and min values to plot
  geom_text(aes(label = ifelse(Lengths == max(Lengths),
    paste0("Max = ", Lengths), "")), 
    hjust = -0.5,
    size = 3,
    color = "black") + 
  geom_text(aes(label = ifelse(Lengths == min(Lengths),
    Lengths, "")),
    vjust = 1.5,
    size = 3,
    color = "black") + 
  geom_text(aes(x = 11.5, y = 1, label = "Min = "),
    size = 3,
    color = "black") +
  guides(colour = guide_legend(override.aes = aes(label = "")))


### CODE COMMENTS ###
#[1]. To see a description of the functions used in this code and how they work please refer 
#     to the code comments made at Figure 3.1 (Chapter 3).
```

From the scatter plot (Figure \@ref(fig:fig41)), we see that from the 48 bottom trawl fishing tows conducted, no fish were measured for 9 (19 %) of the total fishing trips i.e. 12, 22, 24, 28, 30, 40, 43, 44 & 45. Again, this was largely because length measurements were only done when individual species count exceeded 30. Of the top 6 fish species measured, all of the length observations are below 40 cm and they were mostly tightly distributed, which is usually a good signal. This means that none of the data points are *abnormally high* as was the case with the weight data (see Figure \@ref(fig:fig31)). The range for the length distribution is 2 cm to 38 cm. The mean and median length distribution were 12 cm each, which is good as well, as it is likely that the data is not skewed.  

### Assessment of the top 6 fish species lengths across time of day

#### Box plots of the length distributions for the six (6) most common (by amount measured) fish species discarded across time of day.

```{r fig42,  fig.width = 8, fig.height = 5.5, fig.align = "center", fig.cap = "Boxplot of discarded fish species lengths by time of day. Colours are used to represent the different fish species"}

# Plotting data
ggplot(length.data.top.6,
  aes(x = LatinNames, 
    y = Lengths, 
    colour = LatinNames)) +
  geom_boxplot(alpha = 0.5) +
  stat_boxplot(geom = 'errorbar', width = 0.2) +
  theme_bw() +
  theme(panel.background = element_rect(fill = "white",
    colour = "grey50"),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.title = element_blank(),
    legend.position = "bottom",
    legend.text = element_text(face = "italic")) +
  labs(x = "Latin names of fish species",
    y = "Lengths (cm)") +
  facet_wrap(~TimePeriods,
    ncol = 2)

### CODE COMMENTS ###
#[1]. To see a description of the functions used in this code and how they work please refer 
#     to the code comments made at Figure 3.3 (Chapter 3).
```

**Creating a table with the top 6 fish species lengths across time of day**

```{r tab42}

# Creating table
Table.4.2 <- length.data.top.6 %>% 
  group_by(LatinNames,
    TimePeriods) %>% 
  dplyr::summarise(NoMeasured = n(),
    MeanLengths = round(mean(Lengths)),
    MedianLengths = round(median(Lengths)),
    .groups = 'drop')

# Printing table
Table.4.2 %>% 
  kbl(caption = "The top 6 fish species length measurements across time of day") %>%
  kable_classic("striped") %>% 
  row_spec(0, bold = TRUE) %>% 
  column_spec(1, italic = T) %>% 
  kable_styling(fixed_thead = T,
    bootstrap_options = "condensed") 

### CODE COMMENTS ###
#[1]. To see a description of the functions used in this code and how they work please refer 
#     to the code comments made at Table 3.2 (Chapter 3).
```

Of the total discarded fish species measured (2,903) for the top 6 fish species, 1,498 (52 %) are recorded for the day and 1,405 (48 %) for the night (Table \@ref(tab:tab42)). This means that the cumulative fish species measured are marginally higher in the day when compared to the night. Further, we see that the mean lengths by fish species in the day ranged from 9 cm (*Stellifer rastrifer*) to 17 cm (*Cynoscion virescens*). Whereas the mean lengths in the night ranged from 10 cm (*Stellifer rastrifer* and *Bagre bagre*) to 18 cm (*Cynoscion virescens* and *Macrodon ancylodon*). From Figure \@ref(fig:fig42) and Table \@ref(tab:tab42) we see that *Bagre bagre* had the lowest median lengths (9 cm) for the day (with *Stellifer rastrifer*) and night measurements, respectively i.e. for the top 6 fish species examined. While *Cynoscion virescens* and *Macrodon ancylodon* recorded the joint highest median lengths across time of day; day (17 cm) and night (18 cm). Therefore, we conclude that *Cynoscion virescens* and *Macrodon ancylodon* are the largest of the top six discarded fish species examined across time of day as they recorded the highest mean and median length measurements, while *Stellifer rastrifer* and *Bagre bagre* are the smallest i.e. recording the lowest mean and median lengths, respectively, across time of day.  

**Next a similar species assessment will be done but the condition will change from time of day to now fishing depths**

### Assessment of fish species lengths across fishing depths

#### Box plot of the length distribution for the six (6) most common (by amount measured) fish species discarded across fishing depths. 

```{r fig43,  fig.width = 8, fig.height = 5.5, fig.align = "center", fig.cap = "Boxplot of discarded fish species lengths by fishing depths. Colours are used to represent the different fish species"}

ggplot(data = length.data.top.6,
  aes(x = LatinNames, 
    y = Lengths, 
    colour = LatinNames)) +
  geom_boxplot(alpha = 0.5) + 
  stat_boxplot(geom = 'errorbar', width = 0.2) +
  theme_bw() +
  theme(panel.background = element_rect(fill = "white",
    colour = "grey50"),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.title = element_blank(),
    legend.position = "bottom",
    legend.text = element_text(face = "italic"))  +
  labs(x = "Latin names of fish species",
    y = "Lengths (cm)") +
  facet_wrap(.~FishingDepth2) 

### CODE COMMENTS ###
#[1]. To see a description of what the functions in this code are doing please refer to the 
#     code comments made at Figure 3.3 (Chapter 3). The only exception being that time of day is replaced by fishing depths.  
```

**Creating a table of the top 6 fish species lengths across fishing depths**

```{r tab43}

Table.4.3 <- length.data.top.6 %>% 
  group_by(LatinNames,
    FishingDepth2) %>% 
  dplyr::summarise(NoMeasured = n(),
    MeanLengths = round(mean(Lengths)),
    MedianLengths = round(median(Lengths)), 
    .groups = 'drop')

Table.4.3 %>% 
  kbl(caption = "The top 6 fish species length measurements across fishing depths") %>%
  kable_classic("striped") %>% 
  row_spec(0, bold = TRUE) %>% 
  column_spec(1, bold = T) %>% 
  kable_styling(fixed_thead = T,
    bootstrap_options = "condensed")

### CODE COMMENTS ###
#[1]. To see a description of the functions used in this code and how they work please refer 
#     to the code comments made at Table.3.1 (Chapter 3)
```

Of the total discarded fish species measured (2,903) for the top 6 fish species, 1,520 (52 %) are recorded for the deep and 1,383 (48 %) for the shallow Table \@ref(tab:tab43). This means that the cumulative fish species measured are marginally higher in the deep when compared to the shallow. Further, we see that the mean lengths by fish species in the deep ranged from 9 cm (*Stellifer rastrifer*) to 18 cm (*Cynoscion virescens*). The range was the same for the shallow with *Bagre bagre* recording the minimum (9 cm) and once again *Cynoscion virescens* the maximum (18 cm). From Figure \@ref(fig:fig43) and Table \@ref(tab:tab43) we see that *Stellifer rastrifer* had the lowest median lengths (9 cm) for the deep and *Bagre bagre* (8 cm) for the shallow measurements, respectively. While *Cynoscion virescens* recorded the highest median lengths for the deep (17 cm) and the joint highest for the shallow (18 cm) i.e. together with *Macrodon ancylodon*. Therefore, we conclude that *Cynoscion virescens* and *Macrodon ancylodon* are the largest of the top six discarded fish species examined across fishing depths as they recorded the highest mean and median length measurements, while *Stellifer rastrifer* and *Bagre bagre* are the smallest i.e. recording the lowest mean and median lengths, respectively, across fishing depths.  

### Assessment summary

In summary, of the **top 6 species examined** across time of day and fishing depths we found that *Cynoscion virescens* and *Macrodon ancylodon* were often the largest discarded species whereas *Stellifer rastrifer* and *Bagre bagre* were often the smallest discarded species. Four of the top six species measured (i.e. *Macrodon ancylodon*, *Nebris microps*, *Bagre bagre* and *Cynoscion virescens* are commercially viable to the Atlantic seabob and other local fisheries in Guyana. Despite most of the discarded species being juveniles (tiny) and below the common economic length for landing i.e. 25cm, there were some observations of the discarded fish species which were of marketable lengths. This finding was surprising and concerning. In my personal opinion discarding of fish of any size should be disincentivised/disallowed as it is a wastage of valuable marine resources. 

## Research Question 6

**Are the mean lengths for the discarded fish species (ALL) equal across time of day and fishing depths?**

To answer this research question we will now look at the discard fish species - length data for all fish species. This will help us to get an idea of how the lengths are distributed for the entire population and not just a subsample of the data which we used to answer *Research Question 5*.

**The following hypothesis will be tested**

* $H_O$ **(Null hypothesis)** – Mean species lengths are *equal* across time of day and fishing depths. 

* $H_A$ **(Alternate hypothesis)** - Mean species lengths are *not equal* across time of day and fishing depths.

**Again inspection of the data precedes the analysis** 

```{r fig44, fig.width = 8, fig.height = 5.5, fig.align = "center", fig.cap = "Scatter plot of discarded fish species lengths across bottom trawl fishing tows. A total of 48 bottom trawl fishing tows were made. Most of the length observations are below 40 cm. Trichiurus lepturus was the only species consitently above 40 cm."}

xxx <- LengthData %>% 
  filter(Lengths > 40) 

# Plotting data
ggplot(data = LengthData,
  mapping = aes(x = DragID2,
    y = Lengths,
    color = LatinNames)) +
  geom_point(size = 1.2) +
  scale_x_continuous(breaks = seq(from = 1, to = 48)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90,
    vjust = 0.5,
    hjust=1),
    text = element_text(size = 10),
    legend.title = element_blank(),
    legend.position = "bottom",
    legend.margin = margin(),
    legend.text = element_text(face = "italic")) +
  guides(colour = guide_legend(nrow = 4)) +
  labs(x = "Bottom trawl fishing tows",
    y = "Lengths (cm)") +
  ## the code below are used to add the max and min values to plot
  geom_text(aes(label = ifelse(Lengths == max(Lengths),
    paste0("Max = ", Lengths), "")), 
    hjust = -0.5,
    size = 3,
    color = "black") + 
  geom_text(aes(label = ifelse(Lengths == min(Lengths),
    Lengths, "")),
    vjust = 1.5,
    size = 3,
    color = "black") + 
  geom_text(aes(x = 11.75, y = 0.2, label = "Min = "),
    size = 3,
    color = "black") +
  guides(colour = guide_legend(override.aes = aes(label = "")))

### CODE COMMENTS ###
#[1]. Please see the code comments made at Figure 3.1. 
```


```{r fig45, fig.width = 8, fig.height = 5.5, fig.align = "center", fig.cap = "Scatter plot of discarded fish species lengths across bottom trawl fishing tows. A total of 48 bottom trawl fishing tows were made. Most of the length observations are below 40 cm. Trichiurus lepturus was removed."}

# Plotting data without Trichiurus lepturus

LengthData %>% 
  filter(Lengths < 40) %>% 
  ggplot(mapping = aes(x = DragID2,
    y = Lengths,
    color = LatinNames)) +
  geom_point(size = 1.2) +
  scale_x_continuous(breaks = seq(from = 1, to = 48)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90,
    vjust = 0.5,
    hjust=1),
    text = element_text(size = 10),
    legend.title = element_blank(),
    legend.position = "bottom",
    legend.text = element_text(face = "italic")) +
  guides(colour = guide_legend(nrow = 4)) +
  labs(x = "Bottom trawl fishing tows",
    y = "Lengths (cm)") +
## the code below are used to add the max and min values to plot
  geom_text(aes(label = ifelse(Lengths == max(Lengths),
    paste0("Max = ", Lengths), "")), 
    hjust = -0.5,
    size = 3,
    color = "black") + 
  geom_text(aes(label = ifelse(Lengths == min(Lengths),
    Lengths, "")),
    vjust = 1.5,
    size = 3,
    color = "black") + 
  geom_text(aes(x = 11.5, y = 1.1, label = "Min = "),
    size = 3,
    color = "black") +
  guides(colour = guide_legend(override.aes = aes(label = "")))

### CODE COMMENTS ###
#[1]. Please see the code comments made at Figure 3.1. 
```

From the scatter plot (Figure \@ref(fig:fig44)), we see that for the 48 bottom trawl fishing tows conducted, the lengths ranged  between 2 cm to 70 cm. Despite this range most of the points were below 40 cm. The exceptional points are from a single fish species (*Trichiurus lepturus*) which generally grows large. This species was removed (Figure \@ref(fig:fig45)) so that we can better see the distribution. The data points (lengths) for each species seems tightly distributed, which is a good sign. With this confirmation, we can now go ahead with the data analysis. 

**We will now visualize the length distributions using histograms**

### Length distribution for all discarded fish species, across time of day and fishing depths.

#### Time of day

```{r fig46, fig.align = "center", fig.cap = "Histogram of discarded fish species length-distribution by time of day. Colours used to represent the different time of day. To better see the distribution *Trichiurus lepturus* was removed"}

# Removing Trichiurus lepturus
LengthData2 <- LengthData %>% 
  filter(!LatinNames == "Trichiurus lepturus")

# Summary table - time of day
mean.length.tp <- LengthData2 %>% 
  group_by(TimePeriods) %>% 
  dplyr::summarise(MeanLengths = mean(Lengths), .groups = 'drop')

# Initial plot - time of day
ggplot(data = LengthData2,
  aes(Lengths,
    color = TimePeriods,
    fill = TimePeriods)) +
  geom_histogram(alpha = 0.1,
    bins = 20) + 
  theme_bw() +
  theme(legend.justification = c(1,1.1),
    legend.position = c(0.99,1)) +
  scale_fill_brewer(palette = "Set2") +
  labs(x = "Lengths (cm)",
    y = "Counts") +
  geom_vline(data = mean.length.tp,
    aes(xintercept = MeanLengths,
      color = TimePeriods),
    linetype = "dotted",
    size = 0.5) 
```

*Trichiurus lepturus* was the largest discarded fish species with exceptional values (Figure \@ref(fig:fig44)), and therefore was temporarily removed from the data to allow for better visualization and interpretation of summary statistics. However the species will be included in later analysis. From the histogram shown in Figure \@ref(fig:fig46) we can see that the data is reasonably normally distributed. The reason for the bell shape (the mean) being more oriented to the left of the plot is that discarded fish species are mostly small with only a few larger observations. The lengths for the fish species plotted ranged from 2 cm to 38 cm in the day and 2 cm to 31 cm in the night. The mean length for the discarded fish species is lower in the day (12.6 cm), in comparison to the night (13.0 cm). The standard deviations for the means are 5.3 cm (day) and 5.2 cm (night). 

**We will now look at length distributions across fishing depths**

#### Fishing depths

```{r fig47, fig.align = "center", fig.cap = "Histogram of discarded fish species length-distribution by fishing depths. Colours used to represent the different fishing depths. To better see the distribution *Trichiurus lepturus* was removed once again"}

# Summary table - fishing depths
mean.length.fd <- LengthData2 %>% 
  group_by(FishingDepth2) %>% 
  dplyr::summarise(MeanLengths = mean(Lengths), .groups = 'drop')

# Initial plot - fishing depths
ggplot(data = LengthData2,
  aes(Lengths,
    color = FishingDepth2,
    fill = FishingDepth2)) +
  geom_histogram(alpha = 0.1,
    bins = 20) + 
  theme_bw() +
  theme(legend.justification = c(1,1.1),
    legend.position = c(0.99,1)) +
  scale_fill_brewer(palette = "Set2") +
  labs(x = "Lengths (cm)",
    y = "Counts") +
  geom_vline(data = mean.length.fd,
    aes(xintercept = MeanLengths,
      color = FishingDepth2),
    linetype = "dotted",
    size = 0.5) 
```

As a reminder once more, *Trichiurus lepturus* was temporarily removed. From the histogram shown in Figure \@ref(fig:fig47) we can see that again the data is reasonably normally distributed. The reason for the bell shape (the mean) being more oriented to the left of the plot being the same as stated prior i.e. discarded fish species are mostly small with only a few larger observations. The lengths for the fish species plotted ranged from 2 cm to 38 cm in the deep and 3 cm to 31 cm in the shallow. The mean length for the discarded fish species is lower in the deep (12.4 cm), in comparison to the shallow (13.2 cm). The standard deviations for the means are 5.3 cm (deep) and 5.2 cm (shallow). 

**Having viewed the data, we will now run some statistical tests to test the hypotheses**

### Analysis of the mean lengths for discarded fish species across time of day and fishing depths using the **Welch Two Sample t-test**.

**Test assumptions**

This test assumes that the the length observations across time of day (day/night) and fishing depths (deep/shallow) are normally distributed. Fortunately as well, this method is not at all sensitive to deviations from this assumption. Therefore, if the distributions of day/night or deep/shallow are the same e.g. if both distributions are skewed to the right/left. As seen from the histograms (Figures \@ref(fig:fig46) and \@ref(fig:fig47)), the length distribution fits this expectation nicely. Therefore, the analysis will be performed on the actual length variable and no transformation will be required. **As a precautionary measure, this assumption was also tested in chapter 3.2.2 and proven to be accurate**

**How the Welch Two Sample t-test works**

The test statistic, $t_s$, is computed using a method that has the difference between the means in the numerator. This therefore makes the $t_s$ larger as the means move away from each other. The standard error of the difference in the means in this case is denominator. This value decreases as the sample variances decreases or if the size of sample increase. Hence the $t_s$ gets larger as the means move further apart, the variances get smaller, or if the size of the sample increase. The probability of getting the observed $t_s$ value under the **null hypothesis** is computed using the t-distribution.<br><br>


**Conducting the t-tests**

#### Time of day

```{r}
# Welch t.test - time of day
length.ttest.tp <- t.test(Lengths ~ TimePeriods,
  data = LengthData)

length.ttest.tp

### CODE COMMENTS ###
#[1]. The "LengthData" is passed to t.test(). 
#[2]. t.test() is used to analyze the "Lengths" variable against time of day. 
```

The p-value associated with the test is $0.10$, so we fail to reject the null hypothesis ($H_0$) of no difference between the (true) means of the two groups (i.e. time of day; day and night) since the p-value is greater than the usual significance level $alpha = 0.05$. Therefore we conclude based on this data, that there is not enough evidence of a difference between the (true) means of the two groups at the usual significance level of $alpha = 0.05$. 

**We now repeat the test for fishing depths**

#### Fishing depths

```{r}
# Welch t.test - fishing depths
length.ttest.fd <- t.test(Lengths ~ FishingDepth2,
  data = LengthData)

length.ttest.fd

### CODE COMMENTS ###
#[1]. To see a description of what the functions in this code are doing please refer to
#     the code comments at length.ttest.tp. The only exception is "FishingDepth2" 
#     have replaced "TimePeriods". 
```

The p-value associated with the test is $2.695e-12$, therefore we reject the null hypothesis ($H_0$) of there being no difference between the (true) means of the two groups (i.e. fishing depths; deep and shallow) since the p-value is lesser than the usual significance level $alpha = 0.05$. Therefore we conclude based on this data, that there is enough evidence of a difference between the (true) means of the two groups at the usual significance level of $alpha = 0.05$.

### Analysis summary

In summary, from the analysis of the discarded species (ALL) across time of day, we found that there is not enough evidence to reject the null hypothesis ($H_0$) of the *means being equal across time of day*. This was proven by the high p-value ($> 0.05$) obtained from the Welch Two Sample t-tests conducted on the discarded species data across time of day. On the other hand, we did find (based on the data) that there is enough evidence to reject the null hypothesis ($H_0$) of the *means being equal across fishing depths*. This was proven by the low p-value ($> 0.05$) obtained from the Welch Two Sample t-tests conducted on the discard species data across fishing depths. 

## Final remarks 

Chapter 4 was focused on a **Length Analysis** of the discarded fish species caught offshore Guyana. To achieve this a separate dataset [LengthImport][Length distributions of the discarded fish species] containing length measurements was **Joined** to the original data [Discard.data][Weight distributions of the thirty (30) most common fish species (by weight) discarded] used in Chapter 3 which contained the weight measurements for the **Weight Analysis**. This brings me to end of this project where six [research questions][Research Questions] (click link for a recap) were answered across three different submissions.

Also for more details; including answers to these questions, please click on links to your left (i.e. the floating table of contents) to access the respective Chapters. 


<center>**Thanks For Reviewing**</center> 
