# Seabob Models

## CPUE across all fishing tows

### Subsetting and plotting data

```{r 41, fig.cap = "Distribution of seabob cpue across fishing tows"}

target.catch <- SummaryTable %>% 
  filter(CatchCategory == "Target catch")

target.catch %>% 
  ggplot() + 
  geom_histogram(mapping = aes(x = CpueKGHr)) +
  labs(x = "Seabob CPUE (kgs/hr)") +
  theme_bw()

# Converting variables to factors
factor.var <- c("Company",
  "Month",
  "TimePeriods",
  "FishingZones",
  "FishingDepthMtr")

target.catch[,factor.var] <- lapply(target.catch[,factor.var], factor)

glimpse(target.catch)
```

### Predictor = 1 

```{r 4.2}
seabob.glm.1 <- glm(CpueKGHr ~ Company,
  family = gaussian(link = "log"), 
  data = target.catch)

# Print summary
summary(seabob.glm.1)

anova(seabob.glm.1)
```

### Predictors = 2

```{r 4.3}
seabob.glm.2 <- glm(CpueKGHr ~ Company +
    TimePeriods,
  family = gaussian(link = "log"),
  data = target.catch)

# Print summary
summary(seabob.glm.2)
```

### Predictors = 3

```{r 4.4}
seabob.glm.3 <- glm(CpueKGHr ~ Company +
    TimePeriods +
    Month,
  family = gaussian(link = "log"),
  data = target.catch)

# Print summary
summary(seabob.glm.3)
```

### Predictors = 4

```{r 4.5}
seabob.glm.4 <- glm(CpueKGHr ~ Company +
    TimePeriods + 
    Month + 
    FishingZones,
  family = gaussian(link = "log"),
  data = target.catch,
  na.action = na.exclude)

# Print summary
summary(seabob.glm.4)
```

### Predictors = 5

```{r 4.6}
seabob.glm.5 <- glm(CpueKGHr ~ Company +
    TimePeriods + 
    Month + 
    FishingZones +
    FishingDepthMtr,
  family = gaussian(link = "log"),
  data = target.catch)

# Print summary
summary(seabob.glm.5)
```

### Interaction terms = 1

```{r 4.7}
seabob.glm.6 <- glm(CpueKGHr ~ Company +
    TimePeriods +
    Company*TimePeriods,
  family = gaussian(link = "log"), 
  data = target.catch)

# Print summary
summary(seabob.glm.6)
```

### Interaction terms = 2

```{r 4.8}
seabob.glm.7 <- glm(CpueKGHr ~ Company +
    TimePeriods +
    Month +
    Company*TimePeriods +
    Company*Month,
  family = gaussian(link = "log"), 
  data = target.catch)

# Print summary
summary(seabob.glm.7)
```

### Interaction terms = 3

```{r 4.9}
seabob.glm.8 <- glm(CpueKGHr ~ Company +
    TimePeriods +
    Month +
    Company*TimePeriods +
    Company*Month +
    TimePeriods*Month,
  family = gaussian(link = "log"), 
  data = target.catch)

# Print summary
summary(seabob.glm.8)
```

### Interaction terms = 4

```{r 4.10}
seabob.glm.9 <- glm(CpueKGHr ~ Company +
    TimePeriods +
    Month +
    FishingZones +
    Company*TimePeriods +
    Company*Month +
    Company*FishingZones +
    TimePeriods*Month,
  family = gaussian(link = "log"), 
  data = target.catch)

# Print summary
summary(seabob.glm.9)
```

### Interaction terms = 5

```{r 4.11}
seabob.glm.10 <- glm(CpueKGHr ~ Company +
    TimePeriods +
    Month +
    FishingZones +
    Company*TimePeriods +
    Company*Month +
    Company*FishingZones +
    TimePeriods*Month +
    TimePeriods*FishingZones,
  family = gaussian(link = "log"), 
  data = target.catch)

# Print summary
summary(seabob.glm.10)
```

### Interaction terms = 6

```{r 4.12}
seabob.glm.11 <- glm(CpueKGHr ~ Company +
    TimePeriods +
    Month +
    FishingZones +
    Company*TimePeriods +
    Company*Month +
    Company*FishingZones +
    TimePeriods*Month +
    TimePeriods*FishingZones +
    Month*FishingZones,
  family = gaussian(link = "log"), 
  data = target.catch)

# Print summary
summary(seabob.glm.11)
```

### Interaction terms = 7

```{r 4.13}
seabob.glm.12 <- glm(CpueKGHr ~ Company +
    TimePeriods +
    Month +
    FishingZones +
    FishingDepthMtr +
    Company*TimePeriods +
    Company*Month +
    Company*FishingZones +
    Company*FishingDepthMtr +
    TimePeriods*Month +
    TimePeriods*FishingZones +
    TimePeriods*FishingDepthMtr,
  family = gaussian(link = "log"), 
  data = target.catch)

# Print summary
summary(seabob.glm.12)
```

### Interaction terms = 8

```{r 4.14}
seabob.glm.13 <- glm(CpueKGHr ~ Company +
    TimePeriods +
    Month +
    FishingZones +
    FishingDepthMtr +
    Company*TimePeriods +
    Company*Month +
    Company*FishingZones +
    Company*FishingDepthMtr +
    TimePeriods*Month +
    TimePeriods*FishingZones +
    TimePeriods*FishingDepthMtr +
    Month*FishingZones,
  family = gaussian(link = "log"), 
  data = target.catch)

# Print summary
summary(seabob.glm.13)
```

### Interaction terms = 9

```{r 4.15}
seabob.glm.14 <- glm(CpueKGHr ~ Company +
    TimePeriods +
    Month +
    FishingZones +
    FishingDepthMtr +
    Company*TimePeriods +
    Company*Month +
    Company*FishingZones +
    Company*FishingDepthMtr +
    TimePeriods*Month +
    TimePeriods*FishingZones +
    TimePeriods*FishingDepthMtr +
    Month*FishingZones +
    Month*FishingDepthMtr,
  family = gaussian(link = "log"), 
  data = target.catch)

# Print summary
summary(seabob.glm.14)
```

### Interaction terms = 10

```{r 4.16}
seabob.glm.15 <- glm(CpueKGHr ~ Company +
    TimePeriods +
    Month +
    FishingZones +
    FishingDepthMtr +
    Company*TimePeriods +
    Company*Month +
    Company*FishingZones +
    Company*FishingDepthMtr +
    TimePeriods*Month +
    TimePeriods*FishingZones +
    TimePeriods*FishingDepthMtr +
    Month*FishingZones +
    Month*FishingDepthMtr +
    FishingZones*FishingDepthMtr,
  family = gaussian(link = "log"), 
  data = target.catch)

# Print summary
summary(seabob.glm.15)
```

## Model Comparison

```{r 4.17}
rcompanion::compareGLM(seabob.glm.1,
  seabob.glm.2,
  seabob.glm.3,
  seabob.glm.4,
  seabob.glm.5,
  seabob.glm.6,
  seabob.glm.7,
  seabob.glm.8,
  seabob.glm.9,
  seabob.glm.10,
  seabob.glm.11,
  seabob.glm.12,
  seabob.glm.13,
  seabob.glm.14,
  seabob.glm.15) 
```


## Weight proportions across all fishing tows

### Subsetting and plotting data

```{r 4.18, fig.cap = "Distribution of weight proportions across fishing tows"}

target.catch <- SummaryTable %>% 
  filter(CatchCategory == "Target catch")

target.catch %>% 
  ggplot() + 
  geom_histogram(mapping = aes(x = PropWeight)) +
  labs(x = "Weight proportions (kgs)") +
  theme_bw()

# Converting variables to factors
factor.var <- c("Company",
  "Month",
  "TimePeriods",
  "FishingZones",
  "FishingDepthMtr")

target.catch[,factor.var] <- lapply(target.catch[,factor.var], factor)

glimpse(target.catch)
```

### Predictor = 1 

```{r 4.19}
seabob.glm.1 <- glm(PropWeight ~ Company,
  family = gaussian(link = "log"), 
  data = target.catch)

# Print summary
summary(seabob.glm.1)
```

### Predictors = 2

```{r 4.20}
seabob.glm.2 <- glm(PropWeight ~ Company +
    TimePeriods,
  family = gaussian(link = "log"),
  data = target.catch)

# Print summary
summary(seabob.glm.2)
```

### Predictors = 3

```{r 4.21}
seabob.glm.3 <- glm(PropWeight ~ Company +
    TimePeriods +
    Month,
  family = gaussian(link = "log"),
  data = target.catch)

# Print summary
summary(seabob.glm.3)
```

### Predictors = 4

```{r 4.22}
seabob.glm.4 <- glm(PropWeight ~ Company +
    TimePeriods + 
    Month + 
    FishingZones,
  family = gaussian(link = "log"),
  data = target.catch,
  na.action = na.exclude)

# Print summary
summary(seabob.glm.4)
```

### Predictors = 5

```{r 4.23}
seabob.glm.5 <- glm(PropWeight ~ Company +
    TimePeriods + 
    Month + 
    FishingZones +
    FishingDepthMtr,
  family = gaussian(link = "log"),
  data = target.catch)

# Print summary
summary(seabob.glm.5)
```

### Interaction terms = 1

```{r 4.24}
seabob.glm.6 <- glm(PropWeight ~ Company +
    TimePeriods +
    Company*TimePeriods,
  family = gaussian(link = "log"), 
  data = target.catch)

# Print summary
summary(seabob.glm.6)
```

### Interaction terms = 2

```{r 4.25}
seabob.glm.7 <- glm(PropWeight ~ Company +
    TimePeriods +
    Month +
    Company*TimePeriods +
    Company*Month,
  family = gaussian(link = "log"), 
  data = target.catch)

# Print summary
summary(seabob.glm.7)
```

### Interaction terms = 3

```{r 4.26}
seabob.glm.8 <- glm(PropWeight ~ Company +
    TimePeriods +
    Month +
    Company*TimePeriods +
    Company*Month +
    TimePeriods*Month,
  family = gaussian(link = "log"), 
  data = target.catch)

# Print summary
summary(seabob.glm.8)
```

### Interaction terms = 4

```{r 4.27}
seabob.glm.9 <- glm(PropWeight ~ Company +
    TimePeriods +
    Month +
    FishingZones +
    Company*TimePeriods +
    Company*Month +
    Company*FishingZones +
    TimePeriods*Month,
  family = gaussian(link = "log"), 
  data = target.catch)

# Print summary
summary(seabob.glm.9)
```

### Interaction terms = 5

```{r 4.28}
seabob.glm.10 <- glm(PropWeight ~ Company +
    TimePeriods +
    Month +
    FishingZones +
    Company*TimePeriods +
    Company*Month +
    Company*FishingZones +
    TimePeriods*Month +
    TimePeriods*FishingZones,
  family = gaussian(link = "log"), 
  data = target.catch)

# Print summary
summary(seabob.glm.10)
```

### Interaction terms = 6

```{r 4.29}
seabob.glm.11 <- glm(PropWeight ~ Company +
    TimePeriods +
    Month +
    FishingZones +
    Company*TimePeriods +
    Company*Month +
    Company*FishingZones +
    TimePeriods*Month +
    TimePeriods*FishingZones +
    Month*FishingZones,
  family = gaussian(link = "log"), 
  data = target.catch)

# Print summary
summary(seabob.glm.11)
```

### Interaction terms = 7

```{r 4.30}
seabob.glm.12 <- glm(PropWeight ~ Company +
    TimePeriods +
    Month +
    FishingZones +
    FishingDepthMtr +
    Company*TimePeriods +
    Company*Month +
    Company*FishingZones +
    Company*FishingDepthMtr +
    TimePeriods*Month +
    TimePeriods*FishingZones +
    TimePeriods*FishingDepthMtr,
  family = gaussian(link = "log"), 
  data = target.catch)

# Print summary
summary(seabob.glm.12)
```

### Interaction terms = 8

```{r 4.31}
seabob.glm.13 <- glm(PropWeight ~ Company +
    TimePeriods +
    Month +
    FishingZones +
    FishingDepthMtr +
    Company*TimePeriods +
    Company*Month +
    Company*FishingZones +
    Company*FishingDepthMtr +
    TimePeriods*Month +
    TimePeriods*FishingZones +
    TimePeriods*FishingDepthMtr +
    Month*FishingZones,
  family = gaussian(link = "log"), 
  data = target.catch)

# Print summary
summary(seabob.glm.13)
```

### Interaction terms = 9

```{r 4.32}
seabob.glm.14 <- glm(PropWeight ~ Company +
    TimePeriods +
    Month +
    FishingZones +
    FishingDepthMtr +
    Company*TimePeriods +
    Company*Month +
    Company*FishingZones +
    Company*FishingDepthMtr +
    TimePeriods*Month +
    TimePeriods*FishingZones +
    TimePeriods*FishingDepthMtr +
    Month*FishingZones +
    Month*FishingDepthMtr,
  family = gaussian(link = "log"), 
  data = target.catch)

# Print summary
summary(seabob.glm.14)
```

### Interaction terms = 10

```{r 4.33}
seabob.glm.15 <- glm(PropWeight ~ Company +
    TimePeriods +
    Month +
    FishingZones +
    FishingDepthMtr +
    Company*TimePeriods +
    Company*Month +
    Company*FishingZones +
    Company*FishingDepthMtr +
    TimePeriods*Month +
    TimePeriods*FishingZones +
    TimePeriods*FishingDepthMtr +
    Month*FishingZones +
    Month*FishingDepthMtr +
    FishingZones*FishingDepthMtr,
  family = gaussian(link = "log"), 
  data = target.catch)

# Print summary
summary(seabob.glm.15)
```

## Model Comparison

```{r 4.34}
rcompanion::compareGLM(seabob.glm.1,
  seabob.glm.2,
  seabob.glm.3,
  seabob.glm.4,
  seabob.glm.5,
  seabob.glm.6,
  seabob.glm.7,
  seabob.glm.8,
  seabob.glm.9,
  seabob.glm.10,
  seabob.glm.11,
  seabob.glm.12,
  seabob.glm.13,
  seabob.glm.14,
  seabob.glm.15) 
```
