# Seabob Models - Best Models

## CPUE 

### Data modifications

```{r 5.1}
target.catch.cpue <- SummaryTable %>% 
  ungroup() %>%
  # mutate(Company.bv = case_when(Company == "PSI" ~ 1,
  #   Company == "NHS" ~ 0),
  #   TimePeriods.bv = case_when(TimePeriods == "Day" ~ 1,
  #   TimePeriods == "Night" ~ 0)) %>% 
  filter(CatchCategory == "Target catch") %>% 
  dplyr::select(Company,
  Month,
  TimePeriods,
  FishingZones,
  FishingDepthMtr,
  CpueKGHr)

# Converting variables to factors
factor.var <- c("Company",
  "Month",
  "TimePeriods",
  "FishingZones")

target.catch.cpue[,factor.var] <- lapply(target.catch.cpue[,factor.var], factor)

# Removing fishing zones 2 and 5

drop.zones <- c(2, 5)
target.catch.cpue.2 <- target.catch.cpue %>% 
  filter(!FishingZones %in% drop.zones)
```

### Qucik glance at response variable

```{r 5.2}
# Table
table(target.catch.cpue$CpueKGHr) 

# Histogram
hist(target.catch.cpue$CpueKGHr)
```

#### 2 Predictors

```{r 5.3}
cpue.model.1 <- glm(CpueKGHr ~ Month +
    TimePeriods,
  family = gaussian(link = "log"),
  data = target.catch.cpue)
# Print summary
summary(cpue.model.1)
```

#### 2 Predictors with 1 interaction term

```{r 5.4}
cpue.model.2 <- glm(CpueKGHr ~ Month +
    TimePeriods +
    Month*TimePeriods,
  family = gaussian(link = "log"),
  data = target.catch.cpue)

# Print summary
summary(cpue.model.2)
```

#### 3 Predictors

```{r 5.5}
cpue.model.3 <- glm(CpueKGHr ~ TimePeriods +
    FishingDepthMtr +
    FishingZones,
  family = gaussian(link = "log"),
  data = target.catch.cpue.2)

# Print summary
summary(cpue.model.3)
```

#### 3 Predictors and 1 interaction term

```{r 5.6}
cpue.model.4 <- glm(CpueKGHr ~ FishingDepthMtr +
  FishingZones +
  TimePeriods +
  TimePeriods*FishingZones, # Yields a low AIC
  family = gaussian(link = "log"),
  data = target.catch.cpue.2)

# Print summary
summary(cpue.model.4)
```

#### 3 Predictors with 2 interaction term

```{r 5.7}
cpue.model.5 <- glm(CpueKGHr ~ Month +
    TimePeriods +
    FishingDepthMtr +
    Month*TimePeriods +
    FishingDepthMtr*TimePeriods, 
    # FishingDepthMtr*Month, Gives some NA values
  family = gaussian(link = "log"),
  data = target.catch.cpue)

# Print summary
summary(cpue.model.5)
```

#### 3 Predictors with 1 interaction term - Dropping Month*TimePeriods

```{r 5.8}
cpue.model.5 <- glm(CpueKGHr ~ Month +
    TimePeriods +
    FishingDepthMtr +
    # Month*TimePeriods +
    FishingDepthMtr*TimePeriods, 
    # FishingDepthMtr*Month, Gives some NA values
  family = gaussian(link = "log"),
  data = target.catch.cpue)

# Print summary
summary(cpue.model.5)
```

```{r Prof Paulson, echo = FALSE}

# cpue.model.f.5.b <- aov(CpueKGHR ~ Month + TimePeriods + as.factor(FishingZones) + FishingDepthMtr + 
#       Month:TimePeriods + Month:FishingDepthMtr + TimePeriods:as.factor(FishingZones) + 
#       TimePeriods:FishingDepthMtr,
#    data = species.1)
# 
# cpue.model.f.5.a <- aov(log(CpueKGHR)  ~ Month + TimePeriods + FishingZones + FishingDepthMtr + 
#       Month:TimePeriods + Month:FishingDepthMtr + TimePeriods:FishingZones + 
#       TimePeriods:FishingDepthMtr,
#    data = species.1)
# 
# cpue.model.f.5.c <- lm(log(CpueKGHR)  ~ Month + TimePeriods + FishingZones + FishingDepthMtr + 
#       Month:TimePeriods + Month:FishingDepthMtr + TimePeriods:FishingZones + 
#       TimePeriods:FishingDepthMtr,
#    data = species.1)
# 
# plot(cpue.model.f.5.a)
# plot(cpue.model.f.5.b)
# plot(cpue.model.f.5.c)
# # Print summary
# summary.aov(cpue.model.f.5.a)
# summary.aov(cpue.model.f.5.b)
# summary(cpue.model.f.5.c)
# summary(cpue.model.f.5.b)
# 
# table(species.1$FishingZones,species.1$TimePeriods)
# 
# sapply(species.1,data.class)
```

### Model Comparison

```{r 5.8.1}
rcompanion::compareGLM(cpue.model.1,
  cpue.model.2,
  cpue.model.3,
  cpue.model.4,
  cpue.model.5) 
```

## Weight prop. 

### Data modifications

```{r 5.9}
target.catch.prop <- SummaryTable %>% 
  ungroup() %>%
  filter(CatchCategory == "Target catch") %>% 
  dplyr::select(Company,
  FishingDepthMtr,
  FishingZones,
  Month,
  TimePeriods,
  PropWeight)

# Converting variables to factors
factor.var <- c("Company",
  "Month",
  "TimePeriods",
  "FishingZones")

target.catch.prop[,factor.var] <- lapply(target.catch.prop[,factor.var], factor)

# Removing fishing zones 2 and 5
drop.zones <- c(2, 5)
target.catch.prop.2 <- target.catch.prop %>% 
  filter(!FishingZones %in% drop.zones)
```

### Qucik glance at response variable

```{r 5.10}
# Table
table(target.catch.prop$PropWeight) 

# Histogram
hist(target.catch.prop$PropWeight)
```

#### 2 Predictors

```{r 5.11}
prop.model.1 <- glm(PropWeight ~ Month +
    TimePeriods,
  family = gaussian,
  data = target.catch.prop)

# Print summary
summary(prop.model.1)
```

#### 2 Predictors with 1 interaction term

```{r 5.12}
prop.model.2 <- glm(PropWeight ~ Month +
    TimePeriods +
    Month*TimePeriods,
  family = gaussian,
  data = target.catch.prop)

# Print summary
summary(prop.model.2)
```

#### 3 Predictors

```{r 5.13}
prop.model.3 <- glm(PropWeight ~ Month +
    TimePeriods +
    FishingDepthMtr,
  family = gaussian,
  data = target.catch.prop)

# Print summary
summary(prop.model.3)
```

#### 3 Predictors

```{r 5.14}
prop.model.4 <- glm(PropWeight ~ Month +
    FishingDepthMtr +
    FishingZones,
    # TimePeriods, Adding time of day does not influence significance. 
    # Adding Months results in NA values
  family = gaussian,
  data = target.catch.prop.2)

# Print summary
summary(prop.model.4)
```

#### 3 Predictors and 1 interaction term

```{r 5.15}
prop.model.5 <- glm(PropWeight ~ TimePeriods +
  Month +
  FishingDepthMtr + # Increase significance values
  TimePeriods*Month, 
  family = gaussian,
  data = target.catch.prop)

# Print summary
summary(prop.model.5)
```

#### 3 Predictors with 2 interaction term

```{r 5.16}
prop.model.6 <- glm(PropWeight ~ Month +
    TimePeriods +
    FishingDepthMtr +
    Month*TimePeriods +
    FishingDepthMtr*TimePeriods, # Adding fishing zones yields NA values
  family = gaussian,
  data = target.catch.prop)

# Print summary
summary(prop.model.6)
```

### Model Comparison

```{r 5.17}
rcompanion::compareGLM(prop.model.1,
  prop.model.2,
  prop.model.3,
  prop.model.4,
  prop.model.5,
  prop.model.6) 
```


