#  Best CPUE Models - Top 10 Bycatch Species

## Data Modifications 

```{r 6.1}
# Names to remove 
Remove <- c("Multiple species finfish", "Multiple species prawns", "Xiphopenaeus kroyeri")

# Data
Top10Species <- ObserverData %>% 
  group_by(LatinNames, CommonName) %>% 
  dplyr::summarise(NoSampled = n(),
    .groups = 'drop') %>%
  filter(NoSampled >= 10) %>%
  filter(!LatinNames %in% Remove) %>%
  arrange(desc(NoSampled)) %>% 
  head(10)

# Creating a vector of names
Top10names <- Top10Species$LatinNames


# Filtering data to keep species
FilteredSpecies <- ObserverData %>% 
  filter(LatinNames %in% Top10names) %>% 
  group_by(DragID2) %>%  
  mutate(PropWeight = CpueKGHR/sum(CpueKGHR)) %>% 
  ungroup() %>% 
  dplyr::select(LatinNames,
    DragID2,
    CpueKGHR,
    Company,
    Month,
    TimePeriods,
    FishingZones,
    FishingDepthMtr)

# Converting variables to factors
factor.var <- c("Company",
  "Month",
  "TimePeriods",
  "FishingZones")

FilteredSpecies[,factor.var] <- lapply(FilteredSpecies[,factor.var], factor)

# Removing fishing zones 2 and 5
drop.zones <- c(2, 5)
FilteredSpecies <- FilteredSpecies %>% 
  filter(!FishingZones %in% drop.zones) %>% 
  droplevels()
```

## CPUE Model Selection

### Macrodon ancylodon

```{r 6.2}
species.1 <- FilteredSpecies %>% 
  filter(LatinNames == Top10names[1]) %>% 
  # select(-DragID2) %>% 
  dplyr::select(-LatinNames)

# Histogram
hist(species.1$CpueKGHR, breaks = 10)

# Running models
# 2 Predictors
ma.an.1 <- glm(CpueKGHR ~ Month +
    TimePeriods,
  family = gaussian(link = "log"),
  data = species.1)

summary(ma.an.1) # print summary

# 2 Predictors with 1 interaction term
ma.an.2 <- glm(CpueKGHR ~ Month +
    TimePeriods +
    Month*TimePeriods,
  family = gaussian(link = "log"),
  data = species.1)

summary(ma.an.2) # print summary

# 3 Predictors
ma.an.3 <- glm(CpueKGHR ~ TimePeriods +
    FishingDepthMtr +
    FishingZones,
  family = gaussian(link = "log"),
  data = species.1)

summary(ma.an.3) # print summary

# 3 Predictors and 1 interaction term
ma.an.4 <- glm(CpueKGHR ~ FishingDepthMtr +
  FishingZones +
  TimePeriods +
  TimePeriods*FishingZones, # Yields a low AIC
  family = gaussian(link = "log"),
  data = species.1)

summary(ma.an.4) # print summary

# 3 Predictors with 2 interaction term
ma.an.5 <- glm(CpueKGHR ~ Month +
    TimePeriods +
    FishingDepthMtr +
    Month*TimePeriods +
    FishingDepthMtr*TimePeriods, 
    # FishingDepthMtr*Month, Gives some NA values
  family = gaussian(link = "log"),
  data = species.1)

summary(ma.an.5) # print summary

# 2 Predictors
ma.an.1.log <- glm(log(CpueKGHR) ~ Month +
    TimePeriods,
  family = gaussian,
  data = species.1)

summary(ma.an.1.log) # print summary

# 2 Predictors with 1 interaction term
ma.an.2.log <- glm(log(CpueKGHR) ~ Month +
    TimePeriods +
    Month*TimePeriods,
  family = gaussian,
  data = species.1)

summary(ma.an.2.log) # print summary

# 3 Predictors
ma.an.3.log <- glm(log(CpueKGHR) ~ TimePeriods +
    FishingDepthMtr +
    FishingZones,
  family = gaussian,
  data = species.1)

summary(ma.an.3.log) # print summary

# 3 Predictors and 1 interaction term
ma.an.4.log <- glm(log(CpueKGHR) ~ FishingDepthMtr +
  FishingZones +
  TimePeriods +
  TimePeriods*FishingZones, # Yields a low AIC
  family = gaussian,
  data = species.1)

summary(ma.an.4.log) # print summary

# 3 Predictors with 2 interaction term
ma.an.5.log <- glm(log(CpueKGHR) ~ Month +
    TimePeriods +
    FishingDepthMtr +
    Month*TimePeriods +
    FishingDepthMtr*TimePeriods, 
    # FishingDepthMtr*Month, Gives some NA values
  family = gaussian,
  data = species.1)

summary(ma.an.5.log)

# interaction.plot(species.1$Month, species.1$TimePeriods, species.1$CpueKGHR)
```

#### Model Comparison

```{r 6.3}
rcompanion::compareGLM(ma.an.1,
  ma.an.2,
  ma.an.3,
  ma.an.4,
  ma.an.5,
  ma.an.1.log,
  ma.an.2.log,
  ma.an.3.log,
  ma.an.4.log,
  ma.an.5.log)

# Best model = 6
```

### Callinectes ornatus

```{r 6.4}
species.2 <- FilteredSpecies %>% 
  filter(LatinNames == Top10names[2]) %>% 
  dplyr::select(-LatinNames)

# Histogram
hist(species.2$CpueKGHR, breaks = 10)

# Running models
# 2 Predictors
ca.or.1 <- glm(CpueKGHR ~ Month +
    TimePeriods,
  family = gaussian(link = "log"),
  data = species.2)

summary(ca.or.1) # print summary

# 2 Predictors with 1 interaction term
ca.or.2 <- glm(CpueKGHR ~ Month +
    TimePeriods +
    Month*TimePeriods,
  family = gaussian(link = "log"),
  data = species.2)

summary(ca.or.2) # print summary

# 3 Predictors
ca.or.3 <- glm(CpueKGHR ~ TimePeriods +
    FishingDepthMtr +
    FishingZones,
  family = gaussian(link = "log"),
  data = species.2)

summary(ca.or.3) # print summary

# 3 Predictors and 1 interaction term
ca.or.4 <- glm(CpueKGHR ~ FishingDepthMtr +
  FishingZones +
  TimePeriods +
  TimePeriods*FishingZones, # Yields a low AIC
  family = gaussian(link = "log"),
  data = species.2)

summary(ca.or.4) # print summary

# 3 Predictors with 2 interaction term
ca.or.5 <- glm(CpueKGHR ~ Month +
    TimePeriods +
    FishingDepthMtr +
    Month*TimePeriods +
    FishingDepthMtr*TimePeriods, 
    # FishingDepthMtr*Month, Gives some NA values
  family = gaussian(link = "log"),
  data = species.2)

summary(ca.or.5) # print summary

# 2 Predictors
ca.or.1.log <- glm(log(CpueKGHR) ~ Month +
    TimePeriods,
  family = gaussian,
  data = species.2)

summary(ca.or.1.log) # print summary

# 2 Predictors with 1 interaction term
ca.or.2.log <- glm(log(CpueKGHR) ~ Month +
    TimePeriods +
    Month*TimePeriods,
  family = gaussian,
  data = species.2)

summary(ca.or.2.log) # print summary

# 3 Predictors
ca.or.3.log <- glm(log(CpueKGHR) ~ TimePeriods +
    FishingDepthMtr +
    FishingZones,
  family = gaussian,
  data = species.2)

summary(ca.or.3.log) # print summary

# 3 Predictors and 1 interaction term
ca.or.4.log <- glm(log(CpueKGHR) ~ FishingDepthMtr +
  FishingZones +
  TimePeriods +
  TimePeriods*FishingZones, # Yields a low AIC
  family = gaussian,
  data = species.2)

summary(ca.or.4.log) # print summary

# 3 Predictors with 2 interaction term
ca.or.5.log <- glm(log(CpueKGHR) ~ Month +
    TimePeriods +
    FishingDepthMtr +
    Month*TimePeriods +
    FishingDepthMtr*TimePeriods, 
    # FishingDepthMtr*Month, Gives some NA values
  family = gaussian,
  data = species.2)

summary(ca.or.5.log) # print summary
```

#### Model Comparison

```{r 6.5}
rcompanion::compareGLM(ca.or.1,
  ca.or.2,
  ca.or.3,
  ca.or.4,
  ca.or.5,
  ca.or.1.log,
  ca.or.2.log,
  ca.or.3.log,
  ca.or.4.log,
  ca.or.5.log) 

# Best model = 8
```

### Stellifer rastrifer

```{r 6.6}
species.3 <- FilteredSpecies %>% 
  filter(LatinNames == Top10names[3]) %>% 
  dplyr::select(-LatinNames)

# Histogram
hist(species.3$CpueKGHR, breaks = 10)

# Running models
# 2 Predictors
st.ra.1 <- glm(CpueKGHR ~ Month +
    TimePeriods,
  family = gaussian(link = "log"),
  data = species.3)

summary(st.ra.1) # print summary

# 2 Predictors with 1 interaction term
st.ra.2 <- glm(CpueKGHR ~ Month +
    TimePeriods +
    Month*TimePeriods,
  family = gaussian(link = "log"),
  data = species.3)

summary(st.ra.2) # print summary

# 3 Predictors
st.ra.3 <- glm(CpueKGHR ~ TimePeriods +
    FishingDepthMtr +
    FishingZones,
  family = gaussian(link = "log"),
  data = species.3)

summary(st.ra.3) # print summary

# 3 Predictors and 1 interaction term
st.ra.4 <- glm(CpueKGHR ~ FishingDepthMtr +
  FishingZones +
  TimePeriods +
  TimePeriods*FishingZones, # Yields a low AIC
  family = gaussian(link = "log"),
  data = species.3)

summary(st.ra.4) # print summary

# 3 Predictors with 2 interaction term
st.ra.5 <- glm(CpueKGHR ~ Month +
    TimePeriods +
    FishingDepthMtr +
    Month*TimePeriods +
    FishingDepthMtr*TimePeriods, 
    # FishingDepthMtr*Month, Gives some NA values
  family = gaussian(link = "log"),
  data = species.3)

summary(st.ra.5) # print summary
```

#### Model Comparison

```{r 6.7}
rcompanion::compareGLM(st.ra.1,
  st.ra.2,
  st.ra.3,
  st.ra.4,
  st.ra.5) 

# Best model = 4
```

### Stellifer microps

```{r 6.8}
species.4 <- FilteredSpecies %>% 
  filter(LatinNames == Top10names[4]) %>% 
  dplyr::select(-LatinNames)

species.4 <- rbind(species.4, species.1[c(17,41,45),]) # Copying row from species.one
species.4[c(43,44,45),2] = 0.01 # changing value to '0'
species.4 <- species.4 %>% 
  arrange(DragID2) %>% 
  dplyr::select(-DragID2)

# Histogram
hist(species.4$CpueKGHR, breaks = 10)

# Running models
# 2 Predictors
st.mi.1 <- glm(CpueKGHR ~ Month +
    TimePeriods,
  family = gaussian(link = "log"),
  data = species.4)

summary(st.mi.1) # print summary

# 2 Predictors with 1 interaction term
st.mi.2 <- glm(CpueKGHR ~ Month +
    TimePeriods +
    Month*TimePeriods,
  family = gaussian(link = "log"),
  data = species.4)

summary(st.mi.2) # print summary

# 3 Predictors
st.mi.3 <- glm(CpueKGHR ~ TimePeriods +
    FishingDepthMtr +
    FishingZones,
  family = gaussian(link = "log"),
  data = species.4)

summary(st.mi.3) # print summary

# 3 Predictors and 1 interaction term
st.mi.4 <- glm(CpueKGHR ~ FishingDepthMtr +
  FishingZones +
  TimePeriods +
  TimePeriods*FishingZones, # Yields a low AIC
  family = gaussian(link = "log"),
  data = species.4)

summary(st.mi.4) # print summary

# 3 Predictors with 2 interaction term
st.mi.5 <- glm(CpueKGHR ~ Month +
    TimePeriods +
    FishingDepthMtr +
    Month*TimePeriods +
    FishingDepthMtr*TimePeriods, 
    # FishingDepthMtr*Month, Gives some NA values
  family = gaussian(link = "log"),
  data = species.4)

summary(st.mi.5) # print summary
```

#### Model Comparison

```{r 6.9}
rcompanion::compareGLM(st.mi.1,
  st.mi.2,
  st.mi.3,
  st.mi.4,
  st.mi.5) 

# Best model = 1
```

### Cynoscion virescens

```{r 6.10}
species.5 <- FilteredSpecies %>% 
  filter(LatinNames == Top10names[5]) %>% 
  dplyr::select(-LatinNames)

species.5 <- rbind(species.5, species.1[c(17,21,22,23),]) # Copying row from species.one
species.5[c(42,43,44,45),2] = 0.01 # changing value to '0'
species.5 <- species.5 %>% 
  arrange(DragID2) %>% 
  dplyr::select(-DragID2)

# Histogram
hist(species.5$CpueKGHR, breaks = 10)

# Running models
# 2 Predictors
cy.vi.1 <- glm(CpueKGHR ~ Month +
    TimePeriods,
  family = gaussian(link = "log"),
  data = species.5)

summary(cy.vi.1) # print summary

# 2 Predictors with 1 interaction term
cy.vi.2 <- glm(CpueKGHR ~ Month +
    TimePeriods +
    Month*TimePeriods,
  family = gaussian(link = "log"),
  data = species.5)

summary(cy.vi.2) # print summary

# 3 Predictors
cy.vi.3 <- glm(CpueKGHR ~ TimePeriods +
    FishingDepthMtr +
    FishingZones,
  family = gaussian(link = "log"),
  data = species.5)

summary(cy.vi.3) # print summary

# 3 Predictors and 1 interaction term
cy.vi.4 <- glm(CpueKGHR ~ FishingDepthMtr +
  FishingZones +
  TimePeriods +
  TimePeriods*FishingZones, # Yields a low AIC
  family = gaussian(link = "log"),
  data = species.5)

summary(cy.vi.4) # print summary

# 3 Predictors with 2 interaction term
cy.vi.5 <- glm(CpueKGHR ~ Month +
    TimePeriods +
    FishingDepthMtr +
    Month*TimePeriods +
    FishingDepthMtr*TimePeriods, 
    # FishingDepthMtr*Month, Gives some NA values
  family = gaussian(link = "log"),
  data = species.5)

summary(cy.vi.5) # print summary
```

#### Model Comparison

```{r 6.11}
rcompanion::compareGLM(cy.vi.1,
  cy.vi.2,
  cy.vi.3,
  cy.vi.4,
  cy.vi.5) 

# Best model = 3
```

### Symphurus plagusia

```{r 6.12}
species.6 <- FilteredSpecies %>% 
  filter(LatinNames == Top10names[6]) %>% 
  dplyr::select(-LatinNames)

species.6 <- rbind(species.6, species.1[c(7,10,18,21),]) # Copying row from species.one
species.6[c(42,43,44,45),2] = 0.01 # changing value to '0'
species.6 <- species.6 %>% 
  arrange(DragID2) %>% 
  dplyr::select(-DragID2)

# Histogram
hist(species.6$CpueKGHR, breaks = 10)

# Running models
# 2 Predictors
sy.pl.1 <- glm(CpueKGHR ~ Month +
    TimePeriods,
  family = gaussian(link = "log"),
  data = species.6)

summary(sy.pl.1) # print summary

# 2 Predictors with 1 interaction term
sy.pl.2 <- glm(CpueKGHR ~ Month +
    TimePeriods +
    Month*TimePeriods,
  family = gaussian(link = "log"),
  data = species.6)

summary(sy.pl.2) # print summary

# 3 Predictors
sy.pl.3 <- glm(CpueKGHR ~ TimePeriods +
    FishingDepthMtr +
    FishingZones,
  family = gaussian(link = "log"),
  data = species.6)

summary(sy.pl.3) # print summary

# 3 Predictors and 1 interaction term
sy.pl.4 <- glm(CpueKGHR ~ FishingDepthMtr +
  FishingZones +
  TimePeriods +
  TimePeriods*FishingZones, # Yields a low AIC
  family = gaussian(link = "log"),
  data = species.6)

summary(sy.pl.4) # print summary

# 3 Predictors with 2 interaction term
sy.pl.5 <- glm(CpueKGHR ~ Month +
    TimePeriods +
    FishingDepthMtr +
    Month*TimePeriods +
    FishingDepthMtr*TimePeriods, 
    # FishingDepthMtr*Month, Gives some NA values
  family = gaussian(link = "log"),
  data = species.6)

summary(sy.pl.5) # print summary
```

#### Model Comparison

```{r 6.13}
rcompanion::compareGLM(sy.pl.1,
  sy.pl.2,
  sy.pl.3,
  sy.pl.4,
  sy.pl.5) 

# Best model = 5
```

### Bagre bagre

```{r 6.14}
species.7 <- FilteredSpecies %>% 
  filter(LatinNames == Top10names[7]) %>% 
  dplyr::select(-LatinNames)

species.7 <- rbind(species.7, species.1[c(18,21,24,27,45),]) # Copying row from species.one
species.7[c(41,42,43,44,45),2] = 0.01 # changing value to '0'
species.7 <- species.7 %>% 
  arrange(DragID2) %>% 
  dplyr::select(-DragID2)

# Histogram
hist(species.7$CpueKGHR, breaks = 10)

# Running models
# 2 Predictors
ba.ba.1 <- glm(CpueKGHR ~ Month +
    TimePeriods,
  family = gaussian(link = "log"),
  data = species.7)

summary(ba.ba.1) # print summary

# 2 Predictors with 1 interaction term
ba.ba.2 <- glm(CpueKGHR ~ Month +
    TimePeriods +
    Month*TimePeriods,
  family = gaussian(link = "log"),
  data = species.7)

summary(ba.ba.2) # print summary

# 3 Predictors
ba.ba.3 <- glm(CpueKGHR ~ TimePeriods +
    FishingDepthMtr +
    FishingZones,
  family = gaussian(link = "log"),
  data = species.7)

summary(ba.ba.3) # print summary

# 3 Predictors and 1 interaction term
ba.ba.4 <- glm(CpueKGHR ~ FishingDepthMtr +
  FishingZones +
  TimePeriods +
  TimePeriods*FishingZones, # Yields a low AIC
  family = gaussian(link = "log"),
  data = species.7)

summary(ba.ba.4) # print summary

# 3 Predictors with 2 interaction term
ba.ba.5 <- glm(CpueKGHR ~ Month +
    TimePeriods +
    FishingDepthMtr +
    Month*TimePeriods +
    FishingDepthMtr*TimePeriods, 
    # FishingDepthMtr*Month, Gives some NA values
  family = gaussian(link = "log"),
  data = species.7)

summary(ba.ba.5) # print summary
```

#### Model Comparison

```{r 6.15}
rcompanion::compareGLM(ba.ba.1,
  ba.ba.2,
  ba.ba.3,
  ba.ba.4,
  ba.ba.5)

# Best model = 1
```

### Trichiurus lepturus

```{r 6.16}
species.8 <- FilteredSpecies %>% 
  filter(LatinNames == Top10names[8]) %>% 
  dplyr::select(-LatinNames)

species.8 <- rbind(species.8, species.1[c(6,7,35,37,41,45),]) # Copying row from species.one
species.8[c(40,41,42,43,44,45),2] = 0.01 # changing value to '0'
species.8 <- species.8 %>% 
  arrange(DragID2) %>% 
  dplyr::select(-DragID2)

# Histogram
hist(species.8$CpueKGHR, breaks = 10)

# Running models
# 2 Predictors
tr.le.1 <- glm(CpueKGHR ~ Month +
    TimePeriods,
  family = gaussian(link = "log"),
  data = species.8)

summary(tr.le.1) # print summary

# 2 Predictors with 1 interaction term
tr.le.2 <- glm(CpueKGHR ~ Month +
    TimePeriods +
    Month*TimePeriods,
  family = gaussian(link = "log"),
  data = species.8)

summary(tr.le.2) # print summary

# 3 Predictors
tr.le.3 <- glm(CpueKGHR ~ TimePeriods +
    FishingDepthMtr +
    FishingZones,
  family = gaussian(link = "log"),
  data = species.8)

summary(tr.le.3) # print summary

# 3 Predictors and 1 interaction term
tr.le.4 <- glm(CpueKGHR ~ FishingDepthMtr +
  FishingZones +
  TimePeriods +
  TimePeriods*FishingZones, # Yields a low AIC
  family = gaussian(link = "log"),
  data = species.8)

summary(tr.le.4) # print summary

# 3 Predictors with 2 interaction term
tr.le.5 <- glm(CpueKGHR ~ Month +
    TimePeriods +
    FishingDepthMtr +
    Month*TimePeriods +
    FishingDepthMtr*TimePeriods, 
    # FishingDepthMtr*Month, Gives some NA values
  family = gaussian(link = "log"),
  data = species.8)

summary(tr.le.5) # print summary
```

#### Model Comparison

```{r 6.17}
rcompanion::compareGLM(tr.le.1,
  tr.le.2,
  tr.le.3,
  tr.le.4,
  tr.le.5) 

# Best model = 1
```

### Achirus achirus

```{r 6.18}
species.9 <- FilteredSpecies %>% 
  filter(LatinNames == Top10names[9]) %>% 
  dplyr::select(-LatinNames)

species.9 <- rbind(species.9, species.1[c(10,11,13,15,18,21,24,25),]) # Copying row from species.one
species.9[c(38,39,40,41,42,43,44,45),2] = 0.01 # changing value to '0'
species.9 <- species.9 %>% 
  arrange(DragID2) %>% 
  dplyr::select(-DragID2)

# Histogram
hist(species.9$CpueKGHR, breaks = 10)

# Running models
# 2 Predictors
ac.ac.1 <- glm(CpueKGHR ~ Month +
    TimePeriods,
  family = gaussian(link = "log"),
  data = species.9)

summary(ac.ac.1) # print summary

# 2 Predictors with 1 interaction term
ac.ac.2 <- glm(CpueKGHR ~ Month +
    TimePeriods +
    Month*TimePeriods,
  family = gaussian(link = "log"),
  data = species.9)

summary(ac.ac.2) # print summary

# 3 Predictors
ac.ac.3 <- glm(CpueKGHR ~ TimePeriods +
    FishingDepthMtr +
    FishingZones,
  family = gaussian(link = "log"),
  data = species.9)

summary(ac.ac.3) # print summary

# 3 Predictors and 1 interaction term
ac.ac.4 <- glm(CpueKGHR ~ FishingDepthMtr +
  FishingZones +
  TimePeriods +
  TimePeriods*FishingZones, # Yields a low AIC
  family = gaussian(link = "log"),
  data = species.9)

summary(ac.ac.4) # print summary

# 3 Predictors with 2 interaction term
ac.ac.5 <- glm(CpueKGHR ~ Month +
    TimePeriods +
    FishingDepthMtr +
    Month*TimePeriods +
    FishingDepthMtr*TimePeriods, 
    # FishingDepthMtr*Month, Gives some NA values
  family = gaussian(link = "log"),
  data = species.9)

summary(ac.ac.5) # print summary
```

#### Model Comparison

```{r 6.19}
rcompanion::compareGLM(ac.ac.1,
  ac.ac.2,
  ac.ac.3,
  ac.ac.4,
  ac.ac.5) 

# Best model = 3
```

### Paralonchurus brasiliensis

```{r 6.20}
species.10 <- FilteredSpecies %>% 
  filter(LatinNames == Top10names[10]) %>% 
  dplyr::select(-LatinNames)

species.10 <- rbind(species.10, species.1[c(7,17,20,22,23,28,35,39,43,45),]) # Copying row from species.one
species.10[c(36,37,38,39,40,41,42,43,44,45),2] = 0.01 # changing value to '0'
species.10 <- species.10 %>% 
  arrange(DragID2) %>% 
  dplyr::select(-DragID2)

# Histogram
hist(species.10$CpueKGHR, breaks = 10)
 
# ## Manually check for mismatches
# dim(species.4)
# unique(species.1$DragID2) #######data have 45 rows rows 10, 28, 36
# 
# vec1 <- unique(species.1$DragID2)
# vec2 <- unique(species.10$DragID2)
# 
# vec1[!(vec1 %in% vec2)]

# Running models
# 2 Predictors
pa.br.1 <- glm(CpueKGHR ~ Month +
    TimePeriods,
  family = gaussian(link = "log"),
  data = species.10)

summary(pa.br.1) # print summary

# 2 Predictors with 1 interaction term
pa.br.2 <- glm(CpueKGHR ~ Month +
    TimePeriods +
    Month*TimePeriods,
  family = gaussian(link = "log"),
  data = species.10)

summary(pa.br.2) # print summary

# 3 Predictors
pa.br.3 <- glm(CpueKGHR ~ TimePeriods +
    FishingDepthMtr +
    FishingZones,
  family = gaussian(link = "log"),
  data = species.10)

summary(pa.br.3) # print summary

# 3 Predictors and 1 interaction term
pa.br.4 <- glm(CpueKGHR ~ FishingDepthMtr +
  FishingZones +
  TimePeriods +
  TimePeriods*FishingZones, # Yields a low AIC
  family = gaussian(link = "log"),
  data = species.10)

summary(pa.br.4) # print summary

# 3 Predictors with 2 interaction term
pa.br.5 <- glm(CpueKGHR ~ Month +
    TimePeriods +
    FishingDepthMtr +
    Month*TimePeriods +
    FishingDepthMtr*TimePeriods, 
    # FishingDepthMtr*Month, Gives some NA values
  family = gaussian(link = "log"),
  data = species.10)

summary(pa.br.5) # print summary
```

#### Model Comparison

```{r 6.21}
rcompanion::compareGLM(pa.br.1,
  pa.br.2,
  pa.br.3,
  pa.br.4,
  pa.br.5) 

# Best model = 3
```

### Summary
Models 1, 3 and 5 were often selected at the best model. 
