# Non-parametric Tests 

## Top 10 discard species weight prop 

### Data Modifications 

```{r 7.1}
# Names to remove 
Remove <- c("Multiple species finfish", "Multiple species prawns", "Xiphopenaeus kroyeri")

# Data
Top10Species <- ObserverData %>% 
  group_by(LatinNames, CommonName) %>% 
  dplyr::summarise(NoSampled = n(),
    .groups = 'drop') %>%
  filter(NoSampled >= 10) %>%
  filter(!LatinNames %in% Remove) %>%
  arrange(desc(NoSampled)) %>% 
  head(10)

# Creating a vector of names
Top10names <- Top10Species$LatinNames

# Filtering data to keep species
FilteredSpecies <- ObserverData %>% 
  filter(LatinNames %in% Top10names) %>% 
  group_by(DragID2) %>%  
  mutate(PropWeight = CpueKGHR/sum(CpueKGHR)) %>% 
  ungroup() %>% 
  dplyr::select(LatinNames,
    DragID2,
    PropWeight,
    Company,
    Month,
    TimePeriods,
    FishingZones,
    FishingDepthMtr)

# Converting variables to factors
factor.var <- c("Company",
  "Month",
  "TimePeriods",
  "FishingZones")

FilteredSpecies[,factor.var] <- lapply(FilteredSpecies[,factor.var], factor)

# Removing fishing zones 2 and 5
drop.zones <- c(2, 5)
FilteredSpecies <- FilteredSpecies %>% 
  filter(!FishingZones %in% drop.zones)
names(ObserverData)
```

### Macrodon ancylodon

```{r 7.2}
species.1 <- FilteredSpecies %>% 
  filter(LatinNames == Top10names[1]) %>% 
  # select(-DragID2) %>% 
  dplyr::select(-LatinNames)

# Histograms
bks <- c(10, 30, 50, 100, 500, 1000)

for (i in bks){
  hist(species.1$PropWeight, breaks = i)
} 

# Independent variable 1
# Summary statistics 
Summarize(PropWeight ~ Company,
  data = species.1) 

# Plotting data
histogram(~ PropWeight | Company,
          data = species.1,
          layout=c(1,2)) 

## Non-parametric test
(ma.an.1 <- kruskal.test(PropWeight ~ Company,
  data = species.1))

# Independent variable 2
## Summary statistics 
Summarize(PropWeight ~ TimePeriods,
  data = species.1) 

# Plotting data
histogram(~ PropWeight | TimePeriods,
          data = species.1,
          layout=c(1,2)) 

## Non-parametric test
(ma.an.2 <- kruskal.test(PropWeight ~ TimePeriods,
  data = species.1))

# Independent variable 3
## Summary statistics 
Summarize(PropWeight ~ Month,
  data = species.1) 

# Plotting data
histogram(~ PropWeight | Month,
          data = species.1,
          layout=c(3,3)) 

## Non-parametric test
(ma.an.3 <- kruskal.test(PropWeight ~ Month,
  data = species.1))

# Independent variable 4
## Summary statistics 
Summarize(PropWeight ~ FishingZones,
  data = species.1) 

# Plotting data
histogram(~ PropWeight | FishingZones,
          data = species.1,
          layout=c(2,2)) 

## Non-parametric test
(ma.an.4 <- kruskal.test(PropWeight ~ FishingZones,
  data = species.1))

# Independent variable 5
## Summary statistics 
Summarize(PropWeight ~ as.factor(FishingDepthMtr),
  data = species.1) 

# Plotting data
histogram(~ PropWeight | as.factor(FishingDepthMtr),
          data = species.1,
          layout=c(3,3)) 

## Non-parametric test
(ma.an.5 <- kruskal.test(PropWeight ~ as.factor(FishingDepthMtr),
  data = species.1))

# Lowest p-value = Fishing depth (0.07)
```

### Callinectes ornatus

```{r 7.3}
species.2 <- FilteredSpecies %>% 
  filter(LatinNames == Top10names[2]) %>% 
  dplyr::select(-LatinNames)

# Histograms
for (i in bks){
  hist(species.2$PropWeight, breaks = i)
} 

# Independent variable 1
# Summary statistics 
Summarize(PropWeight ~ Company,
  data = species.2) 

# Plotting data
histogram(~ PropWeight | Company,
          data = species.2,
          layout=c(1,2)) 

## Non-parametric test
(ca.or.1 <- kruskal.test(PropWeight ~ Company,
  data = species.2))

# Independent variable 2
## Summary statistics 
Summarize(PropWeight ~ TimePeriods,
  data = species.2) 

# Plotting data
histogram(~ PropWeight | TimePeriods,
          data = species.2,
          layout=c(1,2)) 

## Non-parametric test
(ca.or.2 <- kruskal.test(PropWeight ~ TimePeriods,
  data = species.2))

# Independent variable 3
## Summary statistics 
Summarize(PropWeight ~ Month,
  data = species.2) 

# Plotting data
histogram(~ PropWeight | Month,
          data = species.2,
          layout=c(3,3)) 

## Non-parametric test
(ca.or.3 <- kruskal.test(PropWeight ~ Month,
  data = species.2))

# Independent variable 4
## Summary statistics 
Summarize(PropWeight ~ FishingZones,
  data = species.2) 

# Plotting data
histogram(~ PropWeight | FishingZones,
          data = species.2,
          layout=c(2,2)) 

## Non-parametric test
(ca.or.4 <- kruskal.test(PropWeight ~ FishingZones,
  data = species.2))

# Independent variable 5
## Summary statistics 
Summarize(PropWeight ~ as.factor(FishingDepthMtr),
  data = species.2) 

# Plotting data
histogram(~ PropWeight | as.factor(FishingDepthMtr),
          data = species.2,
          layout=c(3,3)) 

## Non-parametric test
(ca.or.5 <- kruskal.test(PropWeight ~ as.factor(FishingDepthMtr),
  data = species.2))

# Lowest p-value = Fishing Zone, Company and Month(< 0.05)


```

### Stellifer rastrifer

```{r 7.4}
species.3 <- FilteredSpecies %>% 
  filter(LatinNames == Top10names[3]) %>% 
  dplyr::select(-LatinNames)

# Histograms
for (i in bks){
  hist(species.3$PropWeight, breaks = i)
} 

# Independent variable 1
# Summary statistics 
Summarize(PropWeight ~ Company,
  data = species.3) 

# Plotting data
histogram(~ PropWeight | Company,
          data = species.3,
          layout=c(1,2)) 

## Non-parametric test
(st.ra.1 <- kruskal.test(PropWeight ~ Company,
  data = species.3))

# Independent variable 2
## Summary statistics 
Summarize(PropWeight ~ TimePeriods,
  data = species.3) 

# Plotting data
histogram(~ PropWeight | TimePeriods,
          data = species.3,
          layout=c(1,2)) 

## Non-parametric test
(st.ra.2 <- kruskal.test(PropWeight ~ TimePeriods,
  data = species.3))

# Independent variable 3
## Summary statistics 
Summarize(PropWeight ~ Month,
  data = species.3) 

# Plotting data
histogram(~ PropWeight | Month,
          data = species.3,
          layout=c(3,3)) 

## Non-parametric test
(st.ra.3 <- kruskal.test(PropWeight ~ Month,
  data = species.3))

# Independent variable 4
## Summary statistics 
Summarize(PropWeight ~ FishingZones,
  data = species.3) 

# Plotting data
histogram(~ PropWeight | FishingZones,
          data = species.3,
          layout=c(2,2)) 

## Non-parametric test
(st.ra.4 <- kruskal.test(PropWeight ~ FishingZones,
  data = species.3))

# Independent variable 5
## Summary statistics 
Summarize(PropWeight ~ as.factor(FishingDepthMtr),
  data = species.3) 

# Plotting data
histogram(~ PropWeight | as.factor(FishingDepthMtr),
          data = species.3,
          layout=c(3,3)) 

## Non-parametric test
(st.ra.5 <- kruskal.test(PropWeight ~ as.factor(FishingDepthMtr),
  data = species.3))

# Lowest p-value = Company (0.03)
```

### Stellifer microps

```{r 7.5}
species.4 <- FilteredSpecies %>% 
  filter(LatinNames == Top10names[4]) %>% 
  dplyr::select(-LatinNames)

species.4 <- rbind(species.4, species.1[c(17,41,45),]) # Copying row from species.one
species.4[c(43,44,45),2] = 0.01 # changing value to '0'
species.4 <- species.4 %>% 
  arrange(DragID2) %>% 
  dplyr::select(-DragID2)

# Histograms
for (i in bks){
  hist(species.4$PropWeight, breaks = i)
} 

# Independent variable 1
# Summary statistics 
Summarize(PropWeight ~ Company,
  data = species.4) 

# Plotting data
histogram(~ PropWeight | Company,
          data = species.4,
          layout=c(1,2)) 

## Non-parametric test
(st.mi.1 <- kruskal.test(PropWeight ~ Company,
  data = species.4))

# Independent variable 2
## Summary statistics 
Summarize(PropWeight ~ TimePeriods,
  data = species.4) 

# Plotting data
histogram(~ PropWeight | TimePeriods,
          data = species.4,
          layout=c(1,2)) 

## Non-parametric test
(st.mi.2 <- kruskal.test(PropWeight ~ TimePeriods,
  data = species.4))

# Independent variable 3
## Summary statistics 
Summarize(PropWeight ~ Month,
  data = species.4) 

# Plotting data
histogram(~ PropWeight | Month,
          data = species.4,
          layout=c(3,3)) 

## Non-parametric test
(st.mi.3 <- kruskal.test(PropWeight ~ Month,
  data = species.4))

# Independent variable 4
## Summary statistics 
Summarize(PropWeight ~ FishingZones,
  data = species.4) 

# Plotting data
histogram(~ PropWeight | FishingZones,
          data = species.4,
          layout=c(2,2)) 

## Non-parametric test
(st.mi.4 <- kruskal.test(PropWeight ~ FishingZones,
  data = species.4))

# Independent variable 5
## Summary statistics 
Summarize(PropWeight ~ as.factor(FishingDepthMtr),
  data = species.4) 

# Plotting data
histogram(~ PropWeight | as.factor(FishingDepthMtr),
          data = species.4,
          layout=c(3,3)) 

## Non-parametric test
(st.mi.5 <- kruskal.test(PropWeight ~ as.factor(FishingDepthMtr),
  data = species.4))

# Lowest p-value = Company (0.053)
```

### Cynoscion virescens

```{r 7.6}
species.5 <- FilteredSpecies %>% 
  filter(LatinNames == Top10names[5]) %>% 
  dplyr::select(-LatinNames)

species.5 <- rbind(species.5, species.1[c(17,21,22,23),]) # Copying row from species.one
species.5[c(42,43,44,45),2] = 0.01 # changing value to '0'
species.5 <- species.5 %>% 
  arrange(DragID2) %>% 
  dplyr::select(-DragID2)

# Histograms
for (i in bks){
  hist(species.5$PropWeight, breaks = i)
} 

# Independent variable 1
# Summary statistics 
Summarize(PropWeight ~ Company,
  data = species.5) 

# Plotting data
histogram(~ PropWeight | Company,
          data = species.5,
          layout=c(1,2)) 

## Non-parametric test
(cy.vi.1 <- kruskal.test(PropWeight ~ Company,
  data = species.5))

# Independent variable 2
## Summary statistics 
Summarize(PropWeight ~ TimePeriods,
  data = species.5) 

# Plotting data
histogram(~ PropWeight | TimePeriods,
          data = species.5,
          layout=c(1,2)) 

## Non-parametric test
(cy.vi.2 <- kruskal.test(PropWeight ~ TimePeriods,
  data = species.5))

# Independent variable 3
## Summary statistics 
Summarize(PropWeight ~ Month,
  data = species.5) 

# Plotting data
histogram(~ PropWeight | Month,
          data = species.5,
          layout=c(3,3)) 

## Non-parametric test
(cy.vi.3 <- kruskal.test(PropWeight ~ Month,
  data = species.5))

# Independent variable 4
## Summary statistics 
Summarize(PropWeight ~ FishingZones,
  data = species.5) 

# Plotting data
histogram(~ PropWeight | FishingZones,
          data = species.5,
          layout=c(2,2)) 

## Non-parametric test
(cy.vi.4 <- kruskal.test(PropWeight ~ FishingZones,
  data = species.5))

# Independent variable 5
## Summary statistics 
Summarize(PropWeight ~ as.factor(FishingDepthMtr),
  data = species.5) 

# Plotting data
histogram(~ PropWeight | as.factor(FishingDepthMtr),
          data = species.5,
          layout=c(3,3)) 

## Non-parametric test
(cy.vi.5 <- kruskal.test(PropWeight ~ as.factor(FishingDepthMtr),
  data = species.5))

# Lowest p-values = Fishing Zone and Month(< 0.05)
```

### Symphurus plagusia

```{r 7.7}
species.6 <- FilteredSpecies %>% 
  filter(LatinNames == Top10names[6]) %>% 
  dplyr::select(-LatinNames)

species.6 <- rbind(species.6, species.1[c(7,10,18,21),]) # Copying row from species.one
species.6[c(42,43,44,45),2] = 0.01 # changing value to '0'
species.6 <- species.6 %>% 
  arrange(DragID2) %>% 
  dplyr::select(-DragID2)

# Histograms
for (i in bks){
  hist(species.6$PropWeight, breaks = i)
} 

# Independent variable 1
# Summary statistics 
Summarize(PropWeight ~ Company,
  data = species.6) 

# Plotting data
histogram(~ PropWeight | Company,
          data = species.6,
          layout=c(1,2)) 

## Non-parametric test
(sy.pl.1 <- kruskal.test(PropWeight ~ Company,
  data = species.6))

# Independent variable 2
## Summary statistics 
Summarize(PropWeight ~ TimePeriods,
  data = species.6) 

# Plotting data
histogram(~ PropWeight | TimePeriods,
          data = species.6,
          layout=c(1,2)) 

## Non-parametric test
(sy.pl.2 <- kruskal.test(PropWeight ~ TimePeriods,
  data = species.6))

# Independent variable 3
## Summary statistics 
Summarize(PropWeight ~ Month,
  data = species.6) 

# Plotting data
histogram(~ PropWeight | Month,
          data = species.6,
          layout=c(3,3)) 

## Non-parametric test
(sy.pl.3 <- kruskal.test(PropWeight ~ Month,
  data = species.6))

# Independent variable 4
## Summary statistics 
Summarize(PropWeight ~ FishingZones,
  data = species.6) 

# Plotting data
histogram(~ PropWeight | FishingZones,
          data = species.6,
          layout=c(2,2)) 

## Non-parametric test
(sy.pl.4 <- kruskal.test(PropWeight ~ FishingZones,
  data = species.6))

# Independent variable 5
## Summary statistics 
Summarize(PropWeight ~ as.factor(FishingDepthMtr),
  data = species.6) 

# Plotting data
histogram(~ PropWeight | as.factor(FishingDepthMtr),
          data = species.6,
          layout=c(3,3)) 

## Non-parametric test
(sy.pl.5 <- kruskal.test(PropWeight ~ as.factor(FishingDepthMtr),
  data = species.6))

# Lowest p-value = Company (0.09)
```

### Bagre bagre

```{r 7.8}
species.7 <- FilteredSpecies %>% 
  filter(LatinNames == Top10names[7]) %>% 
  dplyr::select(-LatinNames)

species.7 <- rbind(species.7, species.1[c(18,21,24,27,45),]) # Copying row from species.one
species.7[c(41,42,43,44,45),2] = 0.01 # changing value to '0'
species.7 <- species.7 %>% 
  arrange(DragID2) %>% 
  dplyr::select(-DragID2)

# Histograms
for (i in bks){
  hist(species.7$PropWeight, breaks = i)
} 

# Independent variable 1
# Summary statistics 
Summarize(PropWeight ~ Company,
  data = species.7) 

# Plotting data
histogram(~ PropWeight | Company,
          data = species.7,
          layout=c(1,2)) 

## Non-parametric test
(ba.ba.1 <- kruskal.test(PropWeight ~ Company,
  data = species.7))

# Independent variable 2
## Summary statistics 
Summarize(PropWeight ~ TimePeriods,
  data = species.7) 

# Plotting data
histogram(~ PropWeight | TimePeriods,
          data = species.7,
          layout=c(1,2)) 

## Non-parametric test
(ba.ba.2 <- kruskal.test(PropWeight ~ TimePeriods,
  data = species.7))

# Independent variable 3
## Summary statistics 
Summarize(PropWeight ~ Month,
  data = species.7) 

# Plotting data
histogram(~ PropWeight | Month,
          data = species.7,
          layout=c(3,3)) 

## Non-parametric test
(ba.ba.3 <- kruskal.test(PropWeight ~ Month,
  data = species.7))

# Independent variable 4
## Summary statistics 
Summarize(PropWeight ~ FishingZones,
  data = species.7) 

# Plotting data
histogram(~ PropWeight | FishingZones,
          data = species.7,
          layout=c(2,2)) 

## Non-parametric test
(ba.ba.4 <- kruskal.test(PropWeight ~ FishingZones,
  data = species.7))

# Independent variable 5
## Summary statistics 
Summarize(PropWeight ~ as.factor(FishingDepthMtr),
  data = species.7) 

# Plotting data
histogram(~ PropWeight | as.factor(FishingDepthMtr),
          data = species.7,
          layout=c(3,3)) 

## Non-parametric test
(ba.ba.5 <- kruskal.test(PropWeight ~ as.factor(FishingDepthMtr),
  data = species.7))

# Lowest p-value = Fishing depth (0.13)
```

### Trichiurus lepturus

```{r 7.9}
species.8 <- FilteredSpecies %>% 
  filter(LatinNames == Top10names[8]) %>% 
  dplyr::select(-LatinNames)

species.8 <- rbind(species.8, species.1[c(6,7,35,37,41,45),]) # Copying row from species.one
species.8[c(40,41,42,43,44,45),2] = 0.01 # changing value to '0'
species.8 <- species.8 %>% 
  arrange(DragID2) %>% 
  dplyr::select(-DragID2)

# Histograms
for (i in bks){
  hist(species.8$PropWeight, breaks = i)
} 

# Independent variable 1
# Summary statistics 
Summarize(PropWeight ~ Company,
  data = species.8) 

# Plotting data
histogram(~ PropWeight | Company,
          data = species.8,
          layout=c(1,2)) 

## Non-parametric test
(tr.le.1 <- kruskal.test(PropWeight ~ Company,
  data = species.8))

# Independent variable 2
## Summary statistics 
Summarize(PropWeight ~ TimePeriods,
  data = species.8) 

# Plotting data
histogram(~ PropWeight | TimePeriods,
          data = species.8,
          layout=c(1,2)) 

## Non-parametric test
(tr.le.2 <- kruskal.test(PropWeight ~ TimePeriods,
  data = species.8))

# Independent variable 3
## Summary statistics 
Summarize(PropWeight ~ Month,
  data = species.8) 

# Plotting data
histogram(~ PropWeight | Month,
          data = species.8,
          layout=c(3,3)) 

## Non-parametric test
(tr.le.3 <- kruskal.test(PropWeight ~ Month,
  data = species.8))

# Independent variable 4
## Summary statistics 
Summarize(PropWeight ~ FishingZones,
  data = species.8) 

# Plotting data
histogram(~ PropWeight | FishingZones,
          data = species.8,
          layout=c(2,2)) 

## Non-parametric test
(tr.le.4 <- kruskal.test(PropWeight ~ FishingZones,
  data = species.8))

# Independent variable 5
## Summary statistics 
Summarize(PropWeight ~ as.factor(FishingDepthMtr),
  data = species.8) 

# Plotting data
histogram(~ PropWeight | as.factor(FishingDepthMtr),
          data = species.8,
          layout=c(3,3)) 

## Non-parametric test
(tr.le.5 <- kruskal.test(PropWeight ~ as.factor(FishingDepthMtr),
  data = species.8))

# Lowest p-value = Month (< 0.05)
```

### Achirus achirus

```{r 7.10}
species.9 <- FilteredSpecies %>% 
  filter(LatinNames == Top10names[9]) %>% 
  dplyr::select(-LatinNames)

species.9 <- rbind(species.9, species.1[c(10,11,13,15,18,21,24,25),]) # Copying row from species.one
species.9[c(38,39,40,41,42,43,44,45),2] = 0.01 # changing value to '0'
species.9 <- species.9 %>% 
  arrange(DragID2) %>% 
  dplyr::select(-DragID2)

# Histograms
for (i in bks){
  hist(species.9$PropWeight, breaks = i)
} 

# Independent variable 1
# Summary statistics 
Summarize(PropWeight ~ Company,
  data = species.9) 

# Plotting data
histogram(~ PropWeight | Company,
          data = species.9,
          layout=c(1,2)) 

## Non-parametric test
(ac.ac.1 <- kruskal.test(PropWeight ~ Company,
  data = species.9))

# Independent variable 2
## Summary statistics 
Summarize(PropWeight ~ TimePeriods,
  data = species.9) 

# Plotting data
histogram(~ PropWeight | TimePeriods,
          data = species.9,
          layout=c(1,2)) 

## Non-parametric test
(ac.ac.2 <- kruskal.test(PropWeight ~ TimePeriods,
  data = species.9))

# Independent variable 3
## Summary statistics 
Summarize(PropWeight ~ Month,
  data = species.9) 

# Plotting data
histogram(~ PropWeight | Month,
          data = species.9,
          layout=c(3,3)) 

## Non-parametric test
(ac.ac.3 <- kruskal.test(PropWeight ~ Month,
  data = species.9))

# Independent variable 4
## Summary statistics 
Summarize(PropWeight ~ FishingZones,
  data = species.9) 

# Plotting data
histogram(~ PropWeight | FishingZones,
          data = species.9,
          layout=c(2,2)) 

## Non-parametric test
(ac.ac.4 <- kruskal.test(PropWeight ~ FishingZones,
  data = species.9))

# Independent variable 5
## Summary statistics 
Summarize(PropWeight ~ as.factor(FishingDepthMtr),
  data = species.9) 

# Plotting data
histogram(~ PropWeight | as.factor(FishingDepthMtr),
          data = species.9,
          layout=c(3,3)) 

## Non-parametric test
(ac.ac.5 <- kruskal.test(PropWeight ~ as.factor(FishingDepthMtr),
  data = species.9))

# Lowest p-value = Fishing depth (0.03)
```

### Paralonchurus brasiliensis

```{r 7.11}
species.10 <- FilteredSpecies %>% 
  filter(LatinNames == Top10names[10]) %>% 
  dplyr::select(-LatinNames)

species.10 <- rbind(species.10, species.1[c(7,17,20,22,23,28,35,39,43,45),]) # Copying row from species.one
species.10[c(36,37,38,39,40,41,42,43,44,45),2] = 0.01 # changing value to '0'
species.10 <- species.10 %>% 
  arrange(DragID2) %>% 
  dplyr::select(-DragID2)

# Histograms
for (i in bks){
  hist(species.10$PropWeight, breaks = i)
} 
 
# ## Manually check for mismatches
# dim(species.4)
# unique(species.1$DragID2) #######data have 45 rows rows 10, 28, 36
# 
# vec1 <- unique(species.1$DragID2)
# vec2 <- unique(species.10$DragID2)
# 
# vec1[!(vec1 %in% vec2)]

# Independent variable 1
# Summary statistics 
Summarize(PropWeight ~ Company,
  data = species.10) 

# Plotting data
histogram(~ PropWeight | Company,
          data = species.10,
          layout=c(1,2)) 

## Non-parametric test
(pa.br.1 <- kruskal.test(PropWeight ~ Company,
  data = species.10))

# Independent variable 2
## Summary statistics 
Summarize(PropWeight ~ TimePeriods,
  data = species.10) 

# Plotting data
histogram(~ PropWeight | TimePeriods,
          data = species.10,
          layout=c(1,2)) 

## Non-parametric test
(pa.br.2 <- kruskal.test(PropWeight ~ TimePeriods,
  data = species.10))

# Independent variable 3
## Summary statistics 
Summarize(PropWeight ~ Month,
  data = species.10) 

# Plotting data
histogram(~ PropWeight | Month,
          data = species.10,
          layout=c(3,3)) 

## Non-parametric test
(pa.br.3 <- kruskal.test(PropWeight ~ Month,
  data = species.10))

# Independent variable 4
## Summary statistics 
Summarize(PropWeight ~ FishingZones,
  data = species.10) 

# Plotting data
histogram(~ PropWeight | FishingZones,
          data = species.10,
          layout=c(2,2)) 

## Non-parametric test
(pa.br.4 <- kruskal.test(PropWeight ~ FishingZones,
  data = species.10))

# Independent variable 5
## Summary statistics 
Summarize(PropWeight ~ as.factor(FishingDepthMtr),
  data = species.10) 

# Plotting data
histogram(~ PropWeight | as.factor(FishingDepthMtr),
          data = species.10,
          layout=c(3,3)) 

## Non-parametric test
(pa.br.5 <- kruskal.test(PropWeight ~ as.factor(FishingDepthMtr),
  data = species.10))

# Lowest p-value = Month (0.33)
```

## Model Comparison

```{r 7.12}

Species <- Top10names

Company <- c(ma.an.1$p.value, ca.or.1$p.value, st.ra.1$p.value, st.mi.1$p.value, cy.vi.1$p.value, sy.pl.1$p.value, ba.ba.1$p.value, tr.le.1$p.value, ac.ac.1$p.value, pa.br.1$p.value)


TimePeriods <- c(ma.an.2$p.value, ca.or.2$p.value, st.ra.2$p.value, st.mi.2$p.value, cy.vi.2$p.value, sy.pl.2$p.value, ba.ba.2$p.value, tr.le.2$p.value, ac.ac.2$p.value, pa.br.2$p.value)

Month <- c(ma.an.3$p.value, ca.or.3$p.value, st.ra.3$p.value, st.mi.3$p.value, cy.vi.3$p.value, sy.pl.3$p.value, ba.ba.3$p.value, tr.le.3$p.value, ac.ac.3$p.value, pa.br.3$p.value)

FishingZones <- c(ma.an.4$p.value, ca.or.4$p.value, st.ra.4$p.value, st.mi.4$p.value, cy.vi.4$p.value, sy.pl.4$p.value, ba.ba.4$p.value, tr.le.4$p.value, ac.ac.4$p.value, pa.br.4$p.value)

FishingDepthMtr <- c(ma.an.5$p.value, ca.or.5$p.value, st.ra.5$p.value, st.mi.5$p.value, cy.vi.5$p.value, sy.pl.5$p.value, ba.ba.5$p.value, tr.le.5$p.value, ac.ac.5$p.value, pa.br.5$p.value)


kw.comparison.table <- data.frame(Species, Company, TimePeriods, Month, FishingZones, FishingDepthMtr) %>% 
  mutate_if(is.numeric, round, 3) 

kw.comparison.table[1:10, 1:6] %>%
  mutate(Company = cell_spec(Company, background = ifelse(Company < 0.05, "yellow", " "))) %>% 
  mutate(Month = cell_spec(Month, background = ifelse(Month < 0.05, "yellow", " "))) %>%
  mutate(TimePeriods = cell_spec(TimePeriods, background = ifelse(TimePeriods < 0.05, "yellow", " "))) %>%
  mutate(FishingZones = cell_spec(FishingZones, background = ifelse(FishingZones < 0.05, "yellow", " "))) %>%
  mutate(FishingDepthMtr = cell_spec(FishingDepthMtr, background = ifelse(FishingDepthMtr < 0.05, "yellow", " "))) %>%
  kbl(caption = "Comparison of Kruskal-wallis Test Results for the Top 10 bycatch species",
    booktabs = T, linesep = "", escape = FALSE) %>% 
  add_header_above(c(" " = 1, "P-values" = 5)) %>% 
  kable_paper(full_width = F) %>%
  kable_styling(fixed_thead = T,
    bootstrap_options = c("striped", "condensed")) %>% 
  column_spec(2:6, color = "black") %>% 
  footnote(general = "The p-values < 0.05 are colored yellow.")
```

## All species across bottom trawl tows

### Data Modifications 

```{r 7.13}
discards.prop <- SummaryTable %>% 
  ungroup() %>%
  filter(CatchCategory == "Discarded catch") %>% 
  dplyr::select(Company,
  Month,
  TimePeriods,
  FishingZones,
  FishingDepthMtr,
  PropWeight)

# Converting variables to factors
factor.var <- c("Company",
  "Month",
  "TimePeriods",
  "FishingZones")

discards.prop[,factor.var] <- lapply(discards.prop[,factor.var], factor)

# Removing fishing zones 2 and 5
drop.zones <- c(2, 5)
discards.prop.2 <- discards.prop %>% 
  filter(!FishingZones %in% drop.zones)

# Histogram
hist(discards.prop$PropWeight, breaks = 10)
```

```{r 7.14}
# Independent variable 1
# Summary statistics 
Summarize(PropWeight ~ Company,
  data = discards.prop) 

# Plotting data
histogram(~ PropWeight | Company,
          data = discards.prop,
          layout=c(1,2)) 

## Non-parametric test
(com.model <- kruskal.test(PropWeight ~ Company,
  data = discards.prop))

# Independent variable 2
## Summary statistics 
Summarize(PropWeight ~ TimePeriods,
  data = discards.prop) 

# Plotting data
histogram(~ PropWeight | TimePeriods,
          data = discards.prop,
          layout=c(1,2)) 

## Non-parametric test
(tod.model <- kruskal.test(PropWeight ~ TimePeriods,
  data = discards.prop))

# Independent variable 3
## Summary statistics 
Summarize(PropWeight ~ Month,
  data = discards.prop) 

# Plotting data
histogram(~ PropWeight | Month,
          data = discards.prop,
          layout=c(3,3)) 

## Non-parametric test
(mon.model <- kruskal.test(PropWeight ~ Month,
  data = discards.prop))

# Independent variable 4
## Summary statistics 
Summarize(PropWeight ~ FishingZones,
  data = discards.prop) 

# Plotting data
histogram(~ PropWeight | FishingZones,
          data = discards.prop,
          layout=c(2,2)) 

## Non-parametric test
(fzon.model <- kruskal.test(PropWeight ~ FishingZones,
  data = discards.prop))

# Independent variable 5
## Summary statistics 
Summarize(PropWeight ~ as.factor(FishingDepthMtr),
  data = discards.prop) 

# Plotting data
histogram(~ PropWeight | as.factor(FishingDepthMtr),
          data = discards.prop,
          layout=c(3,3)) 

## Non-parametric test
(fdep.model <- kruskal.test(PropWeight ~ as.factor(FishingDepthMtr),
  data = discards.prop))

# Lowest p-value = Month (0.002)
```

## Model Comparison

```{r 7.15}
Factors <- c("Company", "TimePeriods", "Month", "FishingZones", "FishingDepthMtr")

P.values <- c(com.model$p.value, tod.model$p.value, mon.model$p.value, fzon.model$p.value, fdep.model$p.value)
  
kw.comparison.table.2 <- data.frame(Factors, P.values) %>% 
  mutate_if(is.numeric, round, 3) 

kw.comparison.table.2[1:5, 1:2] %>%
  mutate(P.values = cell_spec(P.values, background = ifelse(P.values < 0.05, "yellow", " "))) %>%
  kbl(caption = "Comparison of Kruskal-wallis Test Results - proportions for all bycatch species",
    booktabs = T,
    linesep = "", 
    escape = FALSE,
    align = "l") %>% 
  kable_paper(full_width = T) %>%
  kable_styling(fixed_thead = T,
    bootstrap_options = c("striped", "condensed")) %>% 
  column_spec(2, color = "black") %>% 
  footnote(general = "The p-values < 0.05 are colored yellow.")
```