# Correlation Analysis for Primary Species{#id.91}

## Weight Proportions 

**Data preparation**

```{r 9.1}

Top10names.plusone <- c("Macrodon ancylodon",        
"Callinectes ornatus",       
"Stellifer rastrifer",       
"Stellifer microps",         
"Cynoscion virescens",       
"Symphurus plagusia",        
"Bagre bagre",               
"Trichiurus lepturus",       
"Achirus achirus",           
"Paralonchurus brasiliensis", 
"Xiphopenaeus kroyeri") 
  
# Modifying data
species.cor <- ObserverData %>% 
  filter(LatinNames %in% Top10names.plusone) %>% 
  group_by(DragID2) %>%  
  mutate(PropWeight = CpueKGHR/sum(CpueKGHR)) %>% 
  ungroup() %>% 
  dplyr::select(LatinNames,
    DragID2,
    PropWeight,
    Company,
    Month,
    TimePeriods,
    FishingZones,
    FishingDepthMtr)

species.cor.2.temp <- species.cor %>%
  pivot_wider(names_from = LatinNames,
    values_from = PropWeight,
    values_fill = 0) 

head(species.cor.2.temp) %>% 
  kbl() %>%
  kable_classic() %>% 
  row_spec(0, bold = TRUE) %>% 
  kable_styling(fixed_thead = T,
    bootstrap_options = "condensed") %>% 
  scroll_box(width = "750px", height = "300px")

species.cor.2 <- species.cor.2.temp[,7:17]

```

### Correlation plots

```{r 9.2, fig.width = 10, fig.height = 8}
# Species correlation plot 
chart.Correlation(species.cor.2, 
  histogram = TRUE,
  pch = 19)
```

### Correlation matrix

```{r 9.3, fig.width = 10, fig.height = 8}

flattenCorrMatrix <- function(cormat, pmat) {
  ut <- upper.tri(cormat)
  data.frame(
    row = rownames(cormat)[row(cormat)[ut]],
    column = rownames(cormat)[col(cormat)[ut]],
    cor  = (cormat)[ut],
    p = pmat[ut])
}

# Drawing a correlogram
cor.mat <- cor(species.cor.2,
  method = "spearman")
cor.mat[lower.tri(cor.mat)] <- NA
cor.mat <- reshape2::melt(cor.mat)
cor.mat <- na.omit(cor.mat)
cor.mat$Var1 <- factor(cor.mat$Var1,levels = unique(cor.mat$Var1))
cor.mat$Var2 <- factor(cor.mat$Var2,levels = unique(cor.mat$Var2))

ggplot(data = cor.mat, aes(Var2, Var1, fill = value)) +
  geom_tile(color = "white") +
  scale_fill_gradientn(colours = brewer.pal(5,"RdYlBu"),
                       name = "Spearman\nCorrelation") +
  theme_bw(base_size = 15) +
  theme(axis.text.x = element_text(
      angle = 45, vjust = 1, hjust = 1
    ),
    legend.title = element_text(size = 16)
    # ,
    # legend.position = "top"
  ) +
  coord_fixed() +
  labs(x = "",y = "")+
  geom_text(aes(label = round(value, 2)), size = 3)

# Flattening matrix
cor.mtx.2 <- rcorr(as.matrix(species.cor.2))

flattenCorrMatrix(round(cor.mtx.2$r,3),
  format(round(cor.mtx.2$P,3),
    scientific = FALSE)) %>% 
  arrange(p)

# Strong negative correlation between Month and fishing depth - likely the reason for NAs in earlier model. 
```

### Significant correlations 

```{r 9.4, fig.width = 10, fig.height = 8, fig.align = "center"}
m <- cor(species.cor.2)

res1 <- cor.mtest(species.cor.2, conf.level = 0.95)

corrplot(m,
  method = "number",
  type = "upper",
  number.cex = 0.7, 
  p.mat = res1$p,
  tl.cex = 0.8) 
```

## CPUE

**Data preparation**

```{r 9.5}

Top10names.plusone <- c("Macrodon ancylodon",        
"Callinectes ornatus",       
"Stellifer rastrifer",       
"Stellifer microps",         
"Cynoscion virescens",       
"Symphurus plagusia",        
"Bagre bagre",               
"Trichiurus lepturus",       
"Achirus achirus",           
"Paralonchurus brasiliensis", 
"Xiphopenaeus kroyeri") 
  
# Modifying data
species.cor <- ObserverData %>% 
  filter(LatinNames %in% Top10names.plusone) %>% 
  group_by(DragID2) %>%  
  mutate(PropWeight = CpueKGHR/sum(CpueKGHR)) %>% 
  ungroup() %>% 
  dplyr::select(LatinNames,
    DragID2,
    CpueKGHR,
    Company,
    Month,
    TimePeriods,
    FishingZones,
    FishingDepthMtr)

species.cor.3.temp <- species.cor %>%
  pivot_wider(names_from = LatinNames,
    values_from = CpueKGHR,
    values_fill = 0) 

head(species.cor.3.temp)

species.cor.3 <- species.cor.3.temp[,7:17]
```

### Correlation plots

```{r 9.6, fig.width = 10, fig.height = 8}
# Species correlation plot 
chart.Correlation(species.cor.3, 
  histogram = TRUE,
  pch = 19)
```

### Correlation matrix

```{r 9.7, fig.width = 10, fig.height = 8}

# Drawing a correlogram
cor.mat <- cor(species.cor.3,
  method = "spearman")
cor.mat[lower.tri(cor.mat)] <- NA
cor.mat <- reshape2::melt(cor.mat)
cor.mat <- na.omit(cor.mat)
cor.mat$Var1 <- factor(cor.mat$Var1,levels = unique(cor.mat$Var1))
cor.mat$Var2 <- factor(cor.mat$Var2,levels = unique(cor.mat$Var2))

ggplot(data = cor.mat, aes(Var2, Var1, fill = value)) +
  geom_tile(color = "white") +
  scale_fill_gradientn(colours = brewer.pal(5,"RdYlBu"),
                       name = "Spearman\nCorrelation") +
  theme_bw(base_size = 15) +
  theme(axis.text.x = element_text(
      angle = 45, vjust = 1, hjust = 1
    ),
    legend.title = element_text(size = 16)
    # ,
    # legend.position = "top"
  ) +
  coord_fixed() +
  labs(x = "",y = "")+
  geom_text(aes(label = round(value, 2)), size = 3)

# Flattening matrix
cor.mtx.2 <- rcorr(as.matrix(species.cor.3))

flattenCorrMatrix(round(cor.mtx.2$r,3),
  format(round(cor.mtx.2$P,3),
    scientific = FALSE)) %>% 
  arrange(p)


# Strong negative correlation between Month and fishing depth - likely the reason for NAs in earlier model. 
```

### Significant correlations 

```{r 9.8, fig.width = 10, fig.height = 8, fig.align = "center"}
m <- cor(species.cor.3)

res1 <- cor.mtest(species.cor.3, conf.level = 0.95)

corrplot(m,
  method = "number",
  type = "upper",
  number.cex = 0.7, 
  p.mat = res1$p,
  tl.cex = 0.8) 
```

## Species with Factor Variables Correlation

## Weight Proportions

```{r 9.9}
species.fv.cor <- species.cor.2.temp[,2:17] %>% 
  mutate(Company = case_when(Company == "PSI" ~ 1,
    Company == "NHS" ~ 0),
    TimePeriods = case_when(TimePeriods == "Day" ~ 1,
      TimePeriods == "Night" ~ 0))
```

### Correlation plots

```{r 9.10, fig.width = 10, fig.height = 8}

# Species correlation plot 
chart.Correlation(species.fv.cor, 
  histogram = TRUE,
  pch = 19)
```

### Correlation matrix

```{r 9.11, fig.width = 10, fig.height = 8}
# Drawing a correlogram
cor.mat <- cor(species.fv.cor,
  method = "spearman")
cor.mat[lower.tri(cor.mat)] <- NA
cor.mat <- reshape2::melt(cor.mat)
cor.mat <- na.omit(cor.mat)
cor.mat$Var1 <- factor(cor.mat$Var1,levels = unique(cor.mat$Var1))
cor.mat$Var2 <- factor(cor.mat$Var2,levels = unique(cor.mat$Var2))

ggplot(data = cor.mat, aes(Var2, Var1, fill = value)) +
  geom_tile(color = "white") +
  scale_fill_gradientn(colours = brewer.pal(5,"RdYlBu"),
                       name = "Spearman\nCorrelation") +
  theme_bw(base_size = 15) +
  theme(axis.text.x = element_text(
      angle = 45, vjust = 1, hjust = 1
    ),
    legend.title = element_text(size = 16)
    # ,
    # legend.position = "top"
  ) +
  coord_fixed() +
  labs(x = "",y = "")+
  geom_text(aes(label = round(value, 2)), size = 3)

# Flattening matrix
cor.mtx.2 <- rcorr(as.matrix(species.fv.cor))

flattenCorrMatrix(round(cor.mtx.2$r,3),
  format(round(cor.mtx.2$P,3),
    scientific = FALSE)) %>% 
  arrange(p)
```

### Significant correlations 

```{r 9.12, fig.width = 10, fig.height = 8, fig.align = "center"}
m <- cor(species.fv.cor)

res1 <- cor.mtest(species.fv.cor, conf.level = 0.95)

corrplot(m,
  method = "number",
  type = "upper",
  number.cex = 0.7, 
  p.mat = res1$p,
  tl.cex = 0.8) 
```

## CPUE

**Data preparation**

```{r 9.13}

species.fv.cor.2 <- species.cor.3.temp[,2:17] %>% 
  mutate(Company = case_when(Company == "PSI" ~ 1,
    Company == "NHS" ~ 0),
    TimePeriods = case_when(TimePeriods == "Day" ~ 1,
      TimePeriods == "Night" ~ 0))

```

### Correlation plots

```{r 9.14, fig.width = 10, fig.height = 8}

# Species correlation plot 
chart.Correlation(species.fv.cor.2, 
  histogram = TRUE,
  pch = 19)
```

### Correlation matrix

```{r 9.15, fig.width = 10, fig.height = 8}

# Drawing a correlogram
cor.mat <- cor(species.fv.cor.2,
  method = "spearman")
cor.mat[lower.tri(cor.mat)] <- NA
cor.mat <- reshape2::melt(cor.mat)
cor.mat <- na.omit(cor.mat)
cor.mat$Var1 <- factor(cor.mat$Var1,levels = unique(cor.mat$Var1))
cor.mat$Var2 <- factor(cor.mat$Var2,levels = unique(cor.mat$Var2))

ggplot(data = cor.mat, aes(Var2, Var1, fill = value)) +
  geom_tile(color = "white") +
  scale_fill_gradientn(colours = brewer.pal(5,"RdYlBu"),
                       name = "Spearman\nCorrelation") +
  theme_bw(base_size = 15) +
  theme(axis.text.x = element_text(
      angle = 45, vjust = 1, hjust = 1
    ),
    legend.title = element_text(size = 16)
    # ,
    # legend.position = "top"
  ) +
  coord_fixed() +
  labs(x = "",y = "")+
  geom_text(aes(label = round(value, 2)), size = 3)

# Flattening matrix
cor.mtx.2 <- rcorr(as.matrix(species.fv.cor.2))

flattenCorrMatrix(round(cor.mtx.2$r,3),
  format(round(cor.mtx.2$P,3),
    scientific = FALSE)) %>% 
  arrange(p)


# Strong negative correlation between Month and fishing depth - likely the reason for NAs in earlier model. 
```

### Significant correlations 

```{r 9.16, fig.width = 10, fig.height = 8, fig.align = "center"}

m <- cor(species.fv.cor.2)

res1 <- cor.mtest(species.fv.cor.2, conf.level = 0.95)

corrplot(m,
  method = "number",
  type = "upper",
  number.cex = 0.7, 
  p.mat = res1$p,
  tl.cex = 0.8) 
```






