# Principal Component Analysis (PCA){#id.101}

**Principal components** are new variables that are constructed as linear combinations or mixtures of the initial variables. 
A PCA converts correlations (or lack thereof) among all of the CPUE and Weight proportions into a 2-D graph. Highly correlated CPUE and Weight proportions will cluster together. 
Also the PCA axis are ranked by order of importance such that differences along the first principal component (PC1) are more important than differences along the second principal component (PC2). This means in clusters = 3 and the difference between clusters on both axes were similar, the clusters along PC1 are deem more different than each other than the clusters along PC2. 

## Prop.Weight Models

```{r 10.1}
# Renaming data
species.pca <- species.cor.2 

# Printing summary of variables
summary(species.pca)
```

```{r 10.2, message = FALSE}

species.pca.2 <- cbind(Row.Names = rownames(species.pca), species.pca)

ggplot(reshape2::melt(species.pca.2, id.vars = "Row.Names"),
  aes(x = value)) +
  geom_histogram(colour = "black", aes(fill = variable)) +
  scale_fill_brewer(palette = "Spectral",
                    name = "Variable")+
  facet_wrap(~variable,
    nrow = 3,
    scales = "free") +
  labs(x = "", 
    y = "Frequency") +
  theme(legend.position = "none") 
```

## PCA

```{r 10.3}
# Before
pca.dat <- PCA(species.pca, 
  graph = TRUE,
  scale.unit = TRUE)

# After 
species.pca.trans <- t(species.pca)
pca.dat.trans <- PCA(species.pca.trans, 
  graph = TRUE,
  scale.unit = TRUE)
```

So what were the PCs generated? How well do they capture the overall variation in the dataset? And how are they stored in the object? Let’s take a look.

```{r 10.4}
# Before
pca.eig <- as.data.frame(format(round(pca.dat$eig,3), scientific = FALSE))

pca.eig

# After
pca.eig.trans <- as.data.frame(format(round(pca.dat.trans$eig,3), scientific = FALSE))

pca.eig.trans
```
  
  
```{r 10.5}
# Before
pca.eig$index <- as.factor(1:nrow(pca.eig))
pca.eig$index.cont <- 1:nrow(pca.eig)

nb.cols <- 11
mycolors <- colorRampPalette(rev(brewer.pal(8, "YlGnBu")))(nb.cols)

#Scree plot
ggplot(pca.eig, 
  aes(x = index,
    y = as.numeric(`percentage of variance`))) +
  geom_bar(stat = "identity",
    aes(fill = index),
    colour = "black") +
  geom_path(aes(x = index.cont, 
    group = 1),
    size = 1,
    colour = "Gray50") +
  geom_point(size = 3) +
  labs(x = "Principal Components",
       y = "Percentage of Variance Explained") +
  scale_fill_manual(values = mycolors) +
  theme_bw(base_size = 15) +
  theme(legend.position = "none")

# After 
pca.eig.trans$index <- as.factor(1:nrow(pca.eig.trans))
pca.eig.trans$index.cont <- 1:nrow(pca.eig.trans)

nb.cols <- 10
mycolors <- colorRampPalette(rev(brewer.pal(8, "YlGnBu")))(nb.cols)

#Scree plot
pca.eig.trans %>% 
ggplot(aes(x = index,
  y =as.numeric(`percentage of variance`))) +
  geom_bar(stat = "identity",
    aes(fill = index),
    colour = "black") +
  geom_path(aes(x = index.cont,
    group = 1),
    size = 1,
    colour = "Gray50") +
  geom_point(size = 3) +
  labs(x = "Principal Components",
       y = "Percentage of Variance Explained") +
  scale_fill_manual(values = mycolors) +
  theme_bw(base_size = 15) +
  theme(legend.position = "none")
```

```{r 10.6}

pca.contrib <- as.data.frame(round(pca.dat$var$contrib, 2))[,1:4]
pca.contrib
```

```{r 10.7}
pca.contrib$var <-
  row.names(pca.contrib) #Turn row names into a variable

pca.contrib <- reshape2::melt(pca.contrib,id.vars = "var") #Melt the dataset
  
total.var <-
  paste0("(",pca.eig$`percentage of variance`[1:4],"% of Variance)",sep = "") #Extract the % of variance explained by each PC

pca.contrib$variable <- factor(pca.contrib$variable,labels =
  paste("PC",1:4," ", total.var,sep = "")) #Append these values to the names of each PC
```


```{r 10.8}
pca.coord <- as.data.frame(round(pca.dat$var$coord, 3))
pca.coord
```

```{r 10.9}
for (i in 1:nrow(pca.contrib))
{
  pca.contrib$dir[i] <- pca.coord[which(row.names(pca.coord) == pca.contrib$var[i]),
                                  grep(as.numeric(substr(pca.contrib$variable[i],3,3)),names(pca.coord))] >
    0
}
pca.contrib
```

```{r 10.10}

ggplot(pca.contrib,aes(x = var,
  y = value)) +
  geom_hline(yintercept = 100 / length(unique(pca.contrib$var)),
             linetype = "dashed") +
  geom_bar(stat = "identity",
    aes(fill = var),
    colour = "black") +
  facet_wrap(~variable,
    nrow = 2,
    scales = "free") +
  # geom_label(aes(label = var,colour = dir)) +
  scale_colour_manual(values = c("red","black"))+
  scale_fill_brewer(palette = "Spectral") +
  theme_bw(base_size = 15) +
  labs(x = NULL, y = "% Contribution to Principal Component", fill = " ") +
  theme(axis.text.x = element_blank(),
    legend.position = "bottom") +
  guides(fill = guide_legend(override.aes =
      aes(label = " "), nrow = 4)) 
```

## CPUE Models

```{r 10.11}
# Renaming data
species.pca.2 <- species.cor.3 

# Printing summary of variables
summary(species.pca.2)
```

```{r 10.12, message = FALSE}

species.pca.3 <- cbind(Row.Names = rownames(species.pca.2), species.pca.2)

ggplot(reshape2::melt(species.pca.3, id.vars = "Row.Names"),
  aes(x = value)) +
  geom_histogram(colour = "black", aes(fill = variable)) +
  scale_fill_brewer(palette = "Spectral",
                    name = "Variable")+
  facet_wrap(~variable,
    nrow = 3,
    scales = "free") +
  labs(x = "", 
    y = "Frequency") +
  theme(legend.position = "none") 
```

## PCA

```{r 10.13}
# Before 
pca.dat.2 <- PCA(species.pca.2, 
  graph = TRUE,
  scale.unit = TRUE)

# After 
species.pca.2.trans <- t(species.pca.2)
pca.dat.2.trans <- PCA(species.pca.2.trans, 
  graph = TRUE,
  scale.unit = TRUE)
```

So what were the PCs generated? How well do they capture the overall variation in the dataset? And how are they stored in the object? Let’s take a look.

```{r 10.14}
# Before
pca.eig.2 <- as.data.frame(format(round(pca.dat.2$eig,3), scientific = FALSE))

pca.eig.2

# After
pca.eig.2.trans <- as.data.frame(format(round(pca.dat.2.trans$eig,3), scientific = FALSE))

pca.eig.2.trans
```
  
  
```{r 10.15}
# Before 
pca.eig.2$index <- as.factor(1:nrow(pca.eig.2))
pca.eig.2$index.cont <- 1:nrow(pca.eig.2)

nb.cols <- 11
mycolors <- colorRampPalette(rev(brewer.pal(8, "YlGnBu")))(nb.cols)

#Scree plot
ggplot(pca.eig.2,aes(x=index,y=as.numeric(`percentage of variance`))) +
  geom_bar(stat = "identity",aes(fill = index),colour = "black") +
  geom_path(aes(x = index.cont, group = 1),size = 1,colour = "Gray50") +
  geom_point(size = 3) +
  labs(x = "Principal Components",
       y = "Percentage of Variance Explained") +
  scale_fill_manual(values = mycolors) +
  theme_bw(base_size = 15) +
  theme(legend.position = "none")

# After
pca.eig.2.trans$index <- as.factor(1:nrow(pca.eig.2.trans))
pca.eig.2.trans$index.cont <- 1:nrow(pca.eig.2.trans)

nb.cols <- 10
mycolors <- colorRampPalette(rev(brewer.pal(8, "YlGnBu")))(nb.cols)

#Scree plot
ggplot(pca.eig.2.trans,aes(x=index,y=as.numeric(`percentage of variance`))) +
  geom_bar(stat = "identity",aes(fill = index),colour = "black") +
  geom_path(aes(x = index.cont, group = 1),size = 1,colour = "Gray50") +
  geom_point(size = 3) +
  labs(x = "Principal Components",
       y = "Percentage of Variance Explained") +
  scale_fill_manual(values = mycolors) +
  theme_bw(base_size = 15) +
  theme(legend.position = "none")

```

```{r 10.16}
pca.contrib.2 <- as.data.frame(round(pca.dat.2$var$contrib, 2))[,1:4]
pca.contrib.2
```

```{r 10.17}
pca.contrib.2$var <-
  row.names(pca.contrib.2) #Turn row names into a variable

pca.contrib.2 <- reshape2::melt(pca.contrib.2,id.vars = "var") #Melt the dataset
  
total.var <-
  paste0("(",pca.eig.2$`percentage of variance`[1:4],"% of Variance)",sep = "") #Extract the % of variance explained by each PC

pca.contrib.2$variable <- factor(pca.contrib.2$variable,labels =
  paste("PC",1:4," ", total.var,sep = "")) #Append these values to the names of each PC
```


```{r 10.18}
pca.coord.2 <- as.data.frame(round(pca.dat.2$var$coord, 3))
pca.coord.2
```

```{r 10.19}
for (i in 1:nrow(pca.contrib.2))
{
  pca.contrib.2$dir[i] <- pca.coord.2[which(row.names(pca.coord) == pca.contrib.2$var[i]),
                                  grep(as.numeric(substr(pca.contrib.2$variable[i],3,3)),names(pca.coord.2))] >
    0
}
pca.contrib.2
```

```{r 10.20}

ggplot(pca.contrib.2,aes(x = var,
  y = value)) +
  geom_hline(yintercept = 100 / length(unique(pca.contrib.2$var)),
             linetype = "dashed") +
  geom_bar(stat = "identity",
    aes(fill = var),
    colour = "black") +
  facet_wrap(~variable,
    nrow = 2,
    scales = "free") +
  # geom_label(aes(label = var,colour = dir)) +
  scale_colour_manual(values = c("red","black"))+
  scale_fill_brewer(palette = "Spectral") +
  theme_bw(base_size = 15) +
  labs(x = NULL, y = "% Contribution to Principal Component", fill = " ") +
  theme(axis.text.x = element_blank(),
    legend.position = "bottom") +
  guides(fill = guide_legend(override.aes =
      aes(label = " "), nrow = 4)) 
```


## Canonical Correspondence Analysis{#id.102}

```{r 10.21, echo=FALSE}
# data(varespec)
# data(varechem)
# ## Common but bad way: use all variables you happen to have in your
# ## environmental data matrix
# vare.cca <- cca(varespec, varechem)
# vare.cca
# plot(vare.cca)
# ## Formula interface and a better model
# vare.cca <- cca(varespec ~ Al + P*(K + Baresoil), data=varechem)
# vare.cca
# plot(vare.cca)
# ## `Partialling out' and `negative components of variance'
# cca(varespec ~ Ca, varechem)
# cca(varespec ~ Ca + Condition(pH), varechem)
```

## First Approach

```{r 10.22}
# Data
cca.data.all <- species.cor %>%
  pivot_wider(names_from = LatinNames,
    values_from = CpueKGHR,
    values_fill = 0) 

# Creating two data frames
cca.1 <- cca.data.all[,7:17]
cca.2 <- cca.data.all[,2:6]

# Fitting model 
cca.model <- cca(cca.1, cca.2)
cca.model

plot(cca.model, xlim = c(-3,3), ylim = c(-1,1))

summary(cca.model)

anova(cca.model)
```

## Second Approach 

```{r}
data.1 <- cca.1[, 7]
data.2 <- cca.1[, c(1:6,8:11)]

# Running model
cc1 <- cc(data.1, data.2)

# display the canonical correlations
cc1$cor

# raw canonical coefficients
cc1[3:4]
```

The raw canonical coefficients are interpreted in a manner analogous to interpreting regression coefficients i.e., for the species *Paralonchurus brasiliensis*, a one unit increase in CPUE leads to a -0.497 decrease in the first canonical variate of the other variables are held constant?

```{r}
# compute canonical loadings
cc2 <- comput(data.1, data.2, cc1)

# display canonical loadings
cc2[3:6]
```
The above correlations are between observed variables and canonical variables which are known as the canonical loadings. These canonical variates are actually a type of latent variable.

```{r}
# tests of canonical dimensions
rho <- cc1$cor
## Define number of observations, number of variables in first set, and number of variables in the second set.
n <- dim(data.1)[1]
p <- length(data.1)
q <- length(data.2)

## Calculate p-values using the F-approximations of different test statistics:
p.asym(rho, n, p, q, tstat = "Wilks")
```

