---
title: "An evaluation of discarded bycatch data collected by at-sea observers (draft #1). - Doc2"
author: "Seion Richardson"
date: "`r format(Sys.time(), '%B %d, %Y')`" 
output: 
  word_document: 
    fig_caption: yes
    toc: yes
    toc_depth: 2
    reference_docx: template.docx
    fig_width: 7
    fig_height: 5
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, fig.height = 4, fig.width = 6, results='asis', warning = FALSE, cache = FALSE)

```


```{r packages, message=FALSE}

library(tidyverse)
library(knitr)
library(RColorBrewer) # display.brewer.all()...to see colors
# library(plyr)
library(captioner)
library(flextable)
library(officer)
# library(skimr)
library(vegan)
library(plotrix)
library(broom)
library(purrr)
```

```{r functions}
source("functionfile.R")
source("Fun2.R")
```

```{r Data, message=FALSE}

obs_wt <- read_csv("observer_weights.csv") 
obs_tp <- read_csv("observer_trips.csv")
obs_fy <- read_csv("observer_fishery.csv")
obs_lt <- read_csv("observer_lengths.csv")
obs_wt_db <- obs_wt %>% 
     filter(groups == "Discarded bycatch") %>% filter(!class == "Unknown") 
obs_wt_db <- obs_wt_db %>% mutate(total_wt_kg = round(total_wt_lbs/2.2, 2), cpue = round(total_wt_kg/hrs_dec, 2)) 

obs_wt_rb <- obs_wt %>% 
     filter(groups == "Retained bycatch") 
obs_wt_tc <- obs_wt %>% 
     filter(groups == "Target catch") 

lengths <- dplyr::inner_join(obs_wt, obs_lt, by=c("drag_all", "sci_name"))

species_curve_t <- read_csv("species_accum_trip.csv")
species_curve_h <- read_csv("species_accum_haul.csv")

time_catch <- read_csv("time_period_catch.csv")
time_cpue <- read_csv("time_period_cpue.csv")
depth_catch <- read_csv("depth_catch.csv")
depth_cpue <- read_csv("depth_cpue.csv")

time_catch_2 <- time_catch %>% gather(day, night, key = "time_period", value = "catch") %>% select(-"difference")

time_cpue_2 <- time_cpue %>% gather(day, night, key = "time_period", value = "cpue") %>% select(-"difference")

depth_catch_2 <-depth_catch %>% gather(shallow, deep, key = "fishing_depth", value = "catch") %>% select(-"difference")

depth_cpue_2 <- depth_cpue %>% gather(shallow, deep, key = "fishing_depth", value = "cpue") %>% select(-"difference")

Cpue_table_tp <- obs_wt_db %>%  
  dplyr::group_by(sci_name, drag_all, drag_period) %>%
  dplyr::summarise(Cpue = round(mean(cpue),2), .groups = 'drop') 

Cpue_table_fd <- obs_wt_db %>%  
  dplyr::group_by(sci_name, drag_all, depth_sd) %>%
  dplyr::summarise(Cpue = round(mean(cpue),2), .groups = 'drop') 
```



```{r mean weight landed by fishing depth}

mean_wt_sd <- obs_wt_db %>% 
  group_by(depth_sd) %>% 
  dplyr::summarise(mean_wt = round(mean(total_wt_kg)), std_dev = round(sd(total_wt_kg)), minimum = min(total_wt_kg), max. = max(total_wt_kg), count = n(), no_trips = n_distinct(drag_all))

(plot1 <- obs_wt_db %>% 
ggplot() +
  geom_boxplot(aes(y = total_wt_kg, x = depth_sd, fill = depth_sd)) +
   geom_text(data = mean_wt_sd, aes(x = depth_sd, y = mean_wt, label = mean_wt), 
              size = 3, vjust = -1.9, hjust = 1.2) +
         theme(panel.background = element_rect(fill = "white", colour = "grey50"), legend.position = "none") +
              labs(x="Fishing depths (fathoms)", y = "Weights (kgs)") + scale_fill_brewer(palette="Pastel1",direction = -1))

# T-Test By fishing depth
catch_sd <- obs_wt_db %>%
  select(trip, depth_sd, sci_name, total_wt_kg) %>%
  group_by(depth_sd, sci_name) %>% 
  dplyr::summarise(mn_ln = mean(total_wt_kg)) 

tstt1_catch_sd <- t.test(mn_ln ~ depth_sd,
       data =  catch_sd) # p-value = 0.0006147314

tab_catch_sd <- map_df(list(tstt1_catch_sd), tidy)

# creating table 

tab1 <- obs_wt_db %>% 
  group_by(depth_sd) %>%
  dplyr::summarise(m_len = round(mean(total_wt_kg)), s_e = round(std.error(total_wt_kg),2), Count = n(), .groups = 'drop')%>% mutate(Difference = round(((12 - 10)/10)*100,2))  

####==============Corrected=====================#####

tstt1_catch_sd_2 <- t.test(total_wt_kg ~ depth_sd,
       data =  obs_wt_db) # p-value 0.0084

```



```{r mean weight landed by time-period}

mean_wt_dp <- obs_wt_db %>% 
  group_by(drag_period) %>% 
  dplyr::summarise(mean_wt = round(mean(total_wt_kg)), std_dev = round(sd(total_wt_kg)), minimum = round(min(total_wt_kg)), max. = max(total_wt_kg), count = n(), no_trips = n_distinct(drag_all))

(plot2 <- obs_wt_db %>% 
    ggplot() +
    geom_boxplot(aes(y = total_wt_kg, x = drag_period, fill = drag_period)) +
    geom_text(data = mean_wt_dp, aes(x = drag_period, y = mean_wt, label = mean_wt), 
              size = 3, vjust = -1.9, hjust = 1.2) +
    theme(panel.background = element_rect(fill = "white", colour = "grey50"), legend.position = "none") +
    labs(x="Time-periods", y = "Weights (kgs)") + scale_fill_brewer(palette="Set2"))

# T-Test By fishing depth
catch_dn <- obs_wt_db %>%
  select(trip, drag_period, sci_name, total_wt_kg) %>%
  group_by(drag_period, sci_name) %>% 
  dplyr::summarise(mn_ln = mean(total_wt_kg)) 

tstt1_catch_dn <- t.test(mn_ln ~ drag_period,
       data =  catch_dn) # p-value 0.7732076



tab_catch_dn <- map_df(list(tstt1_catch_dn), tidy)

# creating table 

tab2 <- obs_wt_db %>% 
  group_by(drag_period) %>%
  dplyr::summarise(m_len = round(mean(total_wt_kg)), s_e = round(std.error(total_wt_kg),2), Count = n(), .groups = 'drop') %>% 
  mutate(Difference = round(((12 - 11)/11)*100,2))  


####==============Corrected=====================#####

tstt1_catch_dn_2 <- t.test(length ~ drag_period,
       data =  lengths) # p-value 0.5997

```

#############################################################################################################################################################################################
\newpage

## Time-periods - Most common species by biomass

<br><br>

```{r Time-periods - Most common species by biomass, message = FALSE, results = 'asis'}

TimePeriodWeight(Data = obs_wt_db %>% filter(sci_name == "Stellifer rastrifer"), Group = drag_period, Quan_var = total_wt_kg, Wvar1 = Median_wt, Wvar2 = Sum_wt, Pos_x = 180, Pos_y1 = 0.08, Pos_y2 = 0.065, hj = 0.85, species = "Stellifer rastrifer")

cat("\n\n\\pagebreak\n")
 
TimePeriodWeight(Data = obs_wt_db %>% filter(sci_name == "Stellifer microps"), Group = drag_period, Quan_var = total_wt_kg, Wvar1 = Median_wt, Wvar2 = Sum_wt, Pos_x = 180, Pos_y1 = 0.08, Pos_y2 = 0.065, hj = 0.85, species = "Stellifer microps")

cat("\n\n\\pagebreak\n")

TimePeriodWeight(Data = obs_wt_db %>% filter(sci_name == "Macrodon ancylodon"), Group = drag_period, Quan_var = total_wt_kg, Wvar1 = Median_wt, Wvar2 = Sum_wt, Pos_x = 180, Pos_y1 = 0.08, Pos_y2 = 0.065, hj = 0.85, species = "Macrodon ancylodon")

cat("\n\n\\pagebreak\n")

TimePeriodWeight(Data = obs_wt_db %>% filter(sci_name == "Cynoscion virescens"), Group = drag_period, Quan_var = total_wt_kg, Wvar1 = Median_wt, Wvar2 = Sum_wt, Pos_x = 180, Pos_y1 = 0.08, Pos_y2 = 0.065, hj = 0.85, species = "Cynoscion virescens")

cat("\n\n\\pagebreak\n")

TimePeriodWeight(Data = obs_wt_db %>% filter(sci_name == "Bagre bagre"), Group = drag_period, Quan_var = total_wt_kg, Wvar1 = Median_wt, Wvar2 = Sum_wt, Pos_x = 180, Pos_y1 = 0.08, Pos_y2 = 0.065, hj = 0.85, species = "Bagre bagre")

cat("\n\n\\pagebreak\n")

TimePeriodWeight(Data = obs_wt_db %>% filter(sci_name == "Symphurus plagusia"), Group = drag_period, Quan_var = total_wt_kg, Wvar1 = Median_wt, Wvar2 = Sum_wt, Pos_x = 180, Pos_y1 = 0.08, Pos_y2 = 0.065, hj = 0.85, species = "Symphurus plagusia")
```

\newpage

## Fishing depths - Most common species by biomass 

<br><br>



```{r Fishing depth - Most common species by biomass, message = FALSE}

TimePeriodWeight(Data = obs_wt_db %>% filter(sci_name == "Stellifer rastrifer"), Group = depth_sd, Quan_var = total_wt_kg, Wvar1 = Median_wt, Wvar2 = Sum_wt, Pos_x = 180, Pos_y1 = 0.08, Pos_y2 = 0.065, hj = 0.85, colr = "Reds", species = "Stellifer rastrifer")

cat("\n\n\\pagebreak\n")

TimePeriodWeight(Data = obs_wt_db %>% filter(sci_name == "Stellifer microps"), Group = depth_sd, Quan_var = total_wt_kg, Wvar1 = Median_wt, Wvar2 = Sum_wt, Pos_x = 180, Pos_y1 = 0.08, Pos_y2 = 0.065, hj = 0.85, colr = "Reds", species = "Stellifer microps")

cat("\n\n\\pagebreak\n")

TimePeriodWeight(Data = obs_wt_db %>% filter(sci_name == "Macrodon ancylodon"), Group = depth_sd, Quan_var = total_wt_kg, Wvar1 = Median_wt, Wvar2 = Sum_wt, Pos_x = 180, Pos_y1 = 0.08, Pos_y2 = 0.065, hj = 0.85, colr = "Reds", species = "Macrodon ancylodon")

cat("\n\n\\pagebreak\n")

TimePeriodWeight(Data = obs_wt_db %>% filter(sci_name == "Cynoscion virescens"), Group = depth_sd, Quan_var = total_wt_kg, Wvar1 = Median_wt, Wvar2 = Sum_wt, Pos_x = 180, Pos_y1 = 0.08, Pos_y2 = 0.065, hj = 0.85, colr = "Reds", species = "Cynoscion virescens")

cat("\n\n\\pagebreak\n")

TimePeriodWeight(Data = obs_wt_db %>% filter(sci_name == "Bagre bagre"), Group = depth_sd, Quan_var = total_wt_kg, Wvar1 = Median_wt, Wvar2 = Sum_wt, Pos_x = 180, Pos_y1 = 0.08, Pos_y2 = 0.065, hj = 0.85, colr = "Reds", species = "Bagre bagre")

cat("\n\n\\pagebreak\n")

TimePeriodWeight(Data = obs_wt_db %>% filter(sci_name == "Symphurus plagusia"), Group = depth_sd, Quan_var = total_wt_kg, Wvar1 = Median_wt, Wvar2 = Sum_wt, Pos_x = 180, Pos_y1 = 0.08, Pos_y2 = 0.065, hj = 0.85, colr = "Reds", species = "Symphurus plagusia")
```


#############################################################################################################################################################################################

\newpage

## Time-periods - Most common species by cpue

<br><br>

```{r mean cpue landed by time-period}

#===================== CPUE PLOT ==========================#
mean_cpue_dp <- obs_wt_db %>% 
  group_by(drag_period) %>% 
  dplyr::summarise(mean_cpue = round(mean(cpue)), std_dev = round(sd(cpue)), minimum = round(min(cpue)), max. = max(cpue), count = n())

(cpue_plot <- obs_wt_db %>% 
    ggplot(mapping = aes(y = cpue, x = drag_period, fill = drag_period)) +
    geom_boxplot() +
    geom_smooth(method = "lm", se=FALSE, color="red", aes(group=1)) +
    geom_text(data = mean_cpue_dp, aes(x = drag_period, y = mean_cpue, label = mean_cpue), 
              size = 3, vjust = -1.9, hjust = 1.2) +
    theme(panel.background = element_rect(fill = "white", colour = "grey50"), legend.position = "none") +
    labs(x="Time-periods",
         y = "Cpue (kgs/hr)",
       title = "Discard Cpue distribution by Time-periods")) 
#================ T-TEST - TIME-PERIOD ====================#

cpue_dn <- obs_wt_db %>%
  select(trip, drag_period, sci_name, cpue) %>%
  group_by(sci_name, drag_period) %>% 
  arrange(sci_name) %>% 
  dplyr::summarise(mn_cpue = mean(cpue)) %>% 
  ungroup() # This step is needed to remove problems with filtering https://community.rstudio.com/t/is-ungroup-recommended-after-every-group-by/5296

cpue_dn <- cpue_dn %>% subset(duplicated(sci_name) | duplicated(sci_name, fromLast=TRUE))

t_test_cpue_dn <- t.test(mn_cpue ~ drag_period, data = cpue_dn, paired = TRUE, conf.level = 0.95) # p-value = 0.1106394

tab_cpue_dn <- map_df(list(t_test_cpue_dn), tidy)

# creating table 

(cpue_tab_dn <- obs_wt_db %>% 
  group_by(drag_period) %>%
  dplyr::summarise(mn_cpue = round(mean(cpue)), s_e = round(std.error(cpue),2), Count = n(), .groups = 'drop') %>% 
  mutate(Difference = round(((3 - 3)/3)*100,2)))  

```


```{r Time-periods - Most common species by cpue, message = FALSE, results = 'asis'}

TimePeriodWeight2(Data = Cpue_table_tp %>% filter(sci_name == "Stellifer rastrifer"), Group = drag_period, Quan_var = Cpue, Quan_var2 = drag_all, Wvar1 = Median_wt, Wvar2 = Trips, species = "Stellifer rastrifer", plot_type = geom_line(), plot_type2 = geom_point())

cat("\n\n\\pagebreak\n")
 
TimePeriodWeight2(Data = Cpue_table_tp %>% filter(sci_name == "Stellifer microps"), Group = drag_period, Quan_var = Cpue, Quan_var2 = drag_all, Wvar1 = Median_wt, Wvar2 = Trips, species = "Stellifer microps", plot_type = geom_line(), plot_type2 = geom_point())

cat("\n\n\\pagebreak\n")

TimePeriodWeight2(Data = Cpue_table_tp %>% filter(sci_name == "Macrodon ancylodon"), Group = drag_period, Quan_var = Cpue, Quan_var2 = drag_all, Wvar1 = Median_wt, Wvar2 = Trips, species = "Macrodon ancylodon", plot_type = geom_line(), plot_type2 = geom_point())

cat("\n\n\\pagebreak\n")

TimePeriodWeight2(Data = Cpue_table_tp %>% filter(sci_name == "Nebris microps"), Group = drag_period, Quan_var = Cpue, Quan_var2 = drag_all, Wvar1 = Median_wt, Wvar2 = Trips, species = "Nebris microps", plot_type = geom_line(), plot_type2 = geom_point())

cat("\n\n\\pagebreak\n")

TimePeriodWeight2(Data = Cpue_table_tp %>% filter(sci_name == "Cynoscion virescens"), Group = drag_period, Quan_var = Cpue, Quan_var2 = drag_all, Wvar1 = Median_wt, Wvar2 = Trips, species = "Cynoscion virescens", plot_type = geom_line(), plot_type2 = geom_point())

cat("\n\n\\pagebreak\n")

TimePeriodWeight2(Data = Cpue_table_tp %>% filter(sci_name == "Gymnura micrura"), Group = drag_period, Quan_var = Cpue, Quan_var2 = drag_all, Wvar1 = Median_wt, Wvar2 = Trips, species = "Gymnura micrura", plot_type = geom_line(), plot_type2 = geom_point())
```

\newpage

## Fishing depths - Most common species by cpue 

<br><br>


```{r mean cpue landed by fishing depth}

#===================== CPUE PLOT ==========================#
mean_cpue_dp <- obs_wt_db %>% 
  group_by(depth_sd) %>% 
  dplyr::summarise(mean_cpue = round(mean(cpue)), std_dev = round(sd(cpue)), minimum = round(min(cpue)), max. = max(cpue), count = n())

(cpue_plot <- obs_wt_db %>% 
    ggplot(mapping = aes(y = cpue, x = depth_sd, fill = depth_sd)) +
    geom_boxplot() +
    geom_smooth(method = "lm", se=FALSE, color="red", aes(group=1)) +
    geom_text(data = mean_cpue_dp, aes(x = depth_sd, y = mean_cpue, label = mean_cpue), 
              size = 3, vjust = -1.9, hjust = 1.2) +
    theme(panel.background = element_rect(fill = "white", colour = "grey50"), legend.position = "none") +
    labs(x="Fishing Depths", y = "Cpue (kgs/hr)", title = "Discard Cpue distribution by Fishing Depths"))
#================ T-TEST - FISHING DEPTH ====================#

cpue_sd <- obs_wt_db %>%
  select(trip, depth_sd, sci_name, cpue) %>%
  group_by(sci_name, depth_sd) %>% 
  arrange(sci_name) %>% 
  dplyr::summarise(mn_cpue = mean(cpue)) %>% 
  ungroup() # This step is needed to remove problems with filtering https://community.rstudio.com/t/is-ungroup-recommended-after-every-group-by/5296

cpue_sd <- cpue_sd %>% subset(duplicated(sci_name) | duplicated(sci_name, fromLast=TRUE))

t_test_cpue_sd <- t.test(mn_cpue ~ depth_sd, data = cpue_sd, paired = TRUE, conf.level = 0.95) # p-value = 0.000004091789

tab_cpue_sd <- map_df(list(t_test_cpue_sd), tidy)

# creating table 

cpue_tab_sd <- obs_wt_db %>% 
  group_by(depth_sd) %>%
  dplyr::summarise(mn_cpue = round(mean(cpue)), s_e = round(std.error(cpue),2), Count = n(), .groups = 'drop') %>% 
  mutate(Difference = round(((3 - 3)/3)*100,2))  

```


```{r Fishing depth - Most common species by cpue, message = FALSE}

TimePeriodWeight2(Data = Cpue_table_fd %>% filter(sci_name == "Stellifer rastrifer"), Group = depth_sd, Quan_var = Cpue, Quan_var2 = drag_all, Wvar1 = Median_wt, Wvar2 = Trips, species = "Stellifer microps", plot_type = geom_line(), plot_type2 = geom_point())

cat("\n\n\\pagebreak\n")
 
TimePeriodWeight2(Data = Cpue_table_fd %>% filter(sci_name == "Stellifer microps"), Group = depth_sd, Quan_var = Cpue, Quan_var2 = drag_all, Wvar1 = Median_wt, Wvar2 = Trips, species = "Stellifer microps", plot_type = geom_line(), plot_type2 = geom_point())

cat("\n\n\\pagebreak\n")

TimePeriodWeight2(Data = Cpue_table_fd %>% filter(sci_name == "Macrodon ancylodon"), Group = depth_sd, Quan_var = Cpue, Quan_var2 = drag_all, Wvar1 = Median_wt, Wvar2 = Trips, species = "Macrodon ancylodon", plot_type = geom_line(), plot_type2 = geom_point())

cat("\n\n\\pagebreak\n")

TimePeriodWeight2(Data = Cpue_table_fd %>% filter(sci_name == "Nebris microps"), Group = depth_sd, Quan_var = Cpue, Quan_var2 = drag_all, Wvar1 = Median_wt, Wvar2 = Trips, species = "Nebris microps", plot_type = geom_line(), plot_type2 = geom_point())

cat("\n\n\\pagebreak\n")

TimePeriodWeight2(Data = Cpue_table_fd %>% filter(sci_name == "Cynoscion virescens"), Group = depth_sd, Quan_var = Cpue, Quan_var2 = drag_all, Wvar1 = Median_wt, Wvar2 = Trips, species = "Cynoscion virescens", plot_type = geom_line(), plot_type2 = geom_point())

cat("\n\n\\pagebreak\n")

TimePeriodWeight2(Data = Cpue_table_fd %>% filter(sci_name == "Gymnura micrura"), Group = depth_sd, Quan_var = Cpue, Quan_var2 = drag_all, Wvar1 = Median_wt, Wvar2 = Trips, species = "Gymnura micrura", plot_type = geom_line(), plot_type2 = geom_point())

cat("\n\n\\pagebreak\n")
```


## Species length comparison - Time-period 

```{r return}
names <- c("Stellifer rastrifer", "Stellifer microps", "Macrodon ancylodon", "Nebris microps", "Bagre bagre", "Cynoscion virescens")

SpeciesComparison(Data = lengths, Group = sci_name, Group2 = drag_period, Quan_var = length, Condition1 = "Day", Condition2 = "Night", names = names, Join = "sci_name",variable = length , by= drag_period)

cat("\n\n\\pagebreak\n")

```


## Species length comparison - Fishing depth

```{r}
namesl <- head(names)
SpeciesComparison(Data = lengths, Group = sci_name, Group2 = depth_sd, Quan_var = length, Condition1 = "Deep", Condition2 = "Shallow", names = names, Join = "sci_name",variable = length, by= depth_sd)

cat("\n\n\\pagebreak\n")
```


## Species weight comparison - Time-period

```{r}
namesw <- c("Stellifer rastrifer", "Stellifer microps", "Macrodon ancylodon", "Cynoscion virescens", "Bagre bagre", "Symphurus plagusia")
# namesw <- head(table_6$`Sceintific names`) # Table referenced from on Research_thesis_draft_2.rmd file

SpeciesComparison(Data = obs_wt_db, Group = sci_name, Group2 = drag_period, Quan_var = total_wt_kg, Condition1 = "Day", Condition2 = "Night", names = namesw, Join = "sci_name",variable = total_wt_kg, by= drag_period)

cat("\n\n\\pagebreak\n")
```


## Species weight comparison - Fishing depths

```{r}
SpeciesComparison(Data = obs_wt_db, Group = sci_name, Group2 = depth_sd, Quan_var = total_wt_kg, Condition1 = "Deep", Condition2 = "Shallow", names = namesw, Join = "sci_name",variable = total_wt_kg, by= depth_sd)

cat("\n\n\\pagebreak\n")
```


## Species cpue comparison - Time-periods

```{r}
source("Fun2.R")

namescr <- c("Stellifer rastrifer", "Stellifer microps", "Macrodon ancylodon", "Nebris microps", "Cynoscion virescens", "Gymnura micrura")
# namescr <- head(table_7$`Sceintific names`)
# namescr <- namescr[c(-4,-6)]

SpeciesComparison3(Data = obs_wt_db, Group = sci_name, Group2 = drag_period, Group3 = trip, Quan_var = cpue, Condition1 = "Day", Condition2 = "Night", names = namescr, Join = "sci_name", variable = mn_ln , by= drag_period, paired = TRUE) # 

cat("\n\n\\pagebreak\n")
```


## Species cpue comparison - Fishing depths

```{r}
# namescr <- head(table_7$`Sceintific names`)
namescr <- namescr[c(-4,-6)]

SpeciesComparison4(Data = obs_wt_db, Group = sci_name, Group2 = depth_sd, Group3 = trip, Quan_var = cpue, Condition1 = "Deep", Condition2 = "Shallow", names = namescr, Join = "sci_name", variable = mn_ln , by= depth_sd, paired=TRUE)

cat("\n\n\\pagebreak\n")
```


### COdes to manually check the number of observations used in T-tests

List of species reference vectors 

what, Vectors (Data | Group (s) | Variables)
Time-period length, names (lengths | time-period | length)
Fishing depth length, namesl (lengths | depth_sd | length)
Time-period and fishing depth biomass, namesw (obs_wt_db | drag_period , depth_sd | total_wt_kg)
Time-period cpue, namescr (obs_wt_db | drag_period | cpue)
Fishing depth cpue, namescr <- namescr[c(-4,-6)] (obs_wt_db | depth_sd | cpue)

```{r}
namescr <- namescr[c(-4,-6)]
```


```{r}

vec <- c(1,2,3,4)

for(i in vec){
  a <- obs_wt_db %>%
  dplyr::filter(sci_name == namescr[i]) %>%
  select(sci_name, depth_sd, trip, cpue) %>%
  dplyr::group_by(trip, depth_sd) %>%
  dplyr::summarise(mn_ln = mean(cpue), .groups = 'drop') 

print(table(a$depth_sd))
}

```




```{r}
sampling_effort <- obs_wt_db %>% 
  select(trip, dep_date, arr_date, das, hrs_dec, total_wt_kg) %>% 
  group_by(trip, dep_date, arr_date, das) %>% 
  dplyr::summarise(sum_wt = round(sum(total_wt_kg)), mean_wt = round(mean(total_wt_kg)), Samples = n())

colnames(sampling_effort) <-c("Trips", "Departure", "Arrival", "Days", "Total weight (kgs)", "Mean weight (kgs)", "n")

sampling_effort %>% 
flextable() %>% 
  autofit() %>% 
  align_text_col(align = "left") %>% 
  align_nottext_col(align = "left") %>% 
  bold(part = "header")


obs_wt_db %>%  
  group_by(depth_sd) %>% 
  dplyr::summarise(n = n())
  
```


```{r}
obs_wt %>% 
  mutate(mt = round(total_wt_lbs/2204, 2)) %>% 
  group_by(groups) %>% 
summarise(wt = sum(mt)) %>% 
  mutate(per = wt/sum(wt)*100)
```


<!-- ```{r} -->

<!-- Loop1 <- c(1,2,3,4,5,6) -->

<!-- for (i in Loop1){ -->

<!--   species_name = paste0("Species",i) -->

<!--   assign(species_name, eval(lengths %>% filter(sci_name == names[i]) %>% -->
<!--   select(sci_name, drag_period, length))) %>% print() -->

<!-- } -->

<!-- ``` -->

```{r}

c <- obs_wt_db %>%
  filter(sci_name == names[1]) %>%
  select(sci_name, drag_period, trip, total_wt_kg) %>%
  dplyr::group_by(trip, drag_period) %>%
  dplyr::summarise(mn_ln = mean(total_wt_kg)) %>%
  # ungroup() %>%
  subset(duplicated(trip) | duplicated(trip, fromLast=TRUE))
```
